### 2012-12-01 paper.tex
Some initial playing around with latex.

\documentclass[a4paper,12pt]{article}
\begin{document}
\title{Mixed Non-Bayesian and DeGroot Learning}
\author{Pedro Barbuda\\pdaquino@umich.edu \and Dan Clark\\ddclark@umich.edu}
\date{December 11, 2012}

\maketitle

\section{Introduction}

\section{The Model}

\subsection{The Network}

(Mixed Non-Bayesian and DeGroot nodes)

\subsection{States and Signals}

We will represent the true state of the world as a probability 
distribution $P_t(x) = m_{t}x, m \in [-2.0, 2.0]$ with support confined to $x \in [0,1]$.  The slope $m_t$ will be the defining characteristic of the distribution.  Thus the parameter $m_t$ is the ``true state of the world'' that each node is trying to determine.

The signals received by nodes in a network will be samples drawn from $P_t$.

\subsection{Representing Belief States}

The foremost difficulty in combining the Non-Bayesian and DeGroot models is that belief of Non-Bayesian nodes is a probability distribution over a finite set of possible states of the world.  For a DeGroot node, belief is simply a single value in $\mathbf{R}$.  Therefore it is necessary to develop a conversion between the belief states of Non-Bayesian and DeGroot nodes.

\subsubsection{Belief in Non-Bayesian Nodes}

To represent a belief about the continuous slope value $m$ for a Non-Bayesian node we discretize $m$ in the following manner.  Let $\{\theta_0, \theta_1,...\theta_n\}, n < \infty$ be the set of belief states for each Non-Bayesian node, where $\theta_i$ correspons to the belief that the slope of $P_t$ is equal to

\subsubsection{Belief in Bayesian Nodes}

\end{document}

### 2012-12-03 paper.tex
Working on getting the model written up.

@@
 \documentclass[a4paper,12pt]{article}
+\usepackage{amsmath} % For 'cases' curly brace
 \begin{document}
@@
 
-We will represent the true state of the world as a probability 
-distribution $P_t(x) = m_{t}x, m \in [-2.0, 2.0]$ with support confined to $x \in [0,1]$.
-The slope $m_t$ will be the defining characteristic of the distribution.
-Thus the parameter $m_t$ is the ``true state of the world'' that each node is trying to determine.
+We will represent the state of the world as a probability distribution:
+\begin{equation}
+P^*(x)=\begin{cases}
+m^* \cdot x & 0 \le x \le 1 \\
+0, & \text{otherwise}
+\end{cases}
+\end{equation}
+The slope $\{ m^* \in \mathbf{R} : -2 \le m^* \le 2 \}$ will be the defining characteristic of the distribution.
+We have chosen to bound $m^*$ between -2 and 2 so that the support of $P_t$  is always over $[0,1]$.
+The value of the parameter $m^*$ is the ``true'' state that each node is trying to learn.
 
-The signals received by nodes in a network will be samples drawn from $P_t$.
+At each timestep $t$, every Non-Bayesian node $i$ will receive a signal $s_{i,t}$ which is a value drawn from $P_t$.
+These observations will be used by the nodes in the network to construct a belief about $m^*$.
 
@@
 The foremost difficulty in combining the Non-Bayesian and DeGroot models is that belief of Non-Bayesian nodes is a probability distribution over a finite set of possible states of the world.
-For a DeGroot node, belief is simply a single value in $\mathbf{R}$.
+
+For a DeGroot node $i$, we represent the belief state of $i$ at time t as a single value 
+$m_{i,t} \in \mathbf{R}$.
+
 Therefore it is necessary to develop a conversion between the belief states of Non-Bayesian and DeGroot nodes.
@@
 
-To represent a belief about the continuous slope value $m$ for a Non-Bayesian node we discretize $m$ in the following manner.
-Let $\{\theta_0, \theta_1,...\theta_n\}, n < \infty$ be the set of belief states for each Non-Bayesian node, where $\theta_i$ correspons to the belief that the slope of $P_t$ is equal to
+To represent a belief about the continuous slope value $m*$ for a Non-Bayesian node we discretize $m$ in the following manner.
+Let $\Theta = \{\theta_0, \theta_1,...\theta_n\}, n < \infty$ be the discrete set of possible states of the world over which each Non-Bayesian node holds a distribution of belief.
+Each $\theta_i$ corresponds to the belief that the slope of $P^*$ is
+\begin{equation} \label{eq:theta_meaning}
+m^* = \frac{4i}{n - 1} - 2
+\end{equation}
+As an example, if we take n = 21 belief states, then we have
+\begin{equation}
+\nonumber
+\begin{cases}
+& \theta_0: m^* = -2.0 \\
+& \theta_1: m^* = -1.9 \\
+& ... \\
+& \theta_{20}: m^* = 2.0
+\end{cases}
+\end{equation}
+For each Non-Bayesian node $i$, the belief at time $t$ that $\theta_i$ is the true state of the world is denoted by $\mu_{i,t}(\theta_i)$.
+Thus $\{ \mu_{i,t}(\theta_1), \mu_{i,t}(\theta_2), ...
+\mu_{i,t}(\theta_n) \}$ is a probability distribution over the set of world states for fixed $i,t$.
 
-\subsubsection{Belief in Bayesian Nodes}
+\subsection{Updating DeGroot Belief}
+DeGroot nodes in our model do not directly receive signals; they act merely as message-passers in the network.
+For the most part our DeGroot nodes behave in a fashion similarly to nodes in a standard DeGroot-style network.
+That is, a DeGroot node's $i$'s belief of the true slope value $m^*$ is given at time $t+1$ as
+\begin{equation} \label{eq:degroot_update}
+m_{i,t+1} = \sum_{j \in N(i)} a_{ij}m_{j,t}
+\end{equation}
+where $N(i)$ denotes the neighbors of $i$.  $a_{ij}$ represents the level of ``trust'' that a DeGroot node $i$ has in neighbor $j$, such that
+
+\begin{equation}
+\nonumber
+\sum_{j \in N(i)} a_{ij} = 1
+\end{equation}
+for all DeGroot nodes $i$.  Thus the DeGroot update in equation \ref{eq:degroot_update} is simply a weighted average of its neighbors beliefs in the previous timestep.
+
+When a DeGroot node a Non-Bayesian neighbor performs an update it must obtain a value 
+$m_{j,t}$ for the belief of this node.  This is calculated as
+
+\begin{equation}
+m_{j,t} = \sum_{k=1}^n\mu_{j,t}(\theta_k)(\frac{4i}{n - 1} - 2)
+\end{equation}
+
+Here we are taking a weighted average of the $m^*$ value represented by each state $\theta_i$ as defined in equation \ref{eq:theta_meaning}, where the weights are given by $j$'s level of belief in each state.
+
+\subsection{Updating Non-Bayesian Belief}
+
+The update of a Non-Bayesian node in our model is handled similarly to the method laid out 
+in Jadbabaie et. al. % @todo[DDC] Figure out references system
+
+% [DDC] Just putting in the equations for the moment.
+
+\begin{equation}
+m_{i,t}(s_i) = \int_\Theta \ell_i(s_i|\theta)d\mu_{i,t}(\theta) = \sum_{i=1}^n \ell_i(s_i|\theta_i)\mu_{i,t}(\theta_i)
+\end{equation}
+
+\begin{equation}
+\mu_{i,t+1}(\theta_i) = a_{ii}\mu_{i,t}(\theta_i)\frac{\ell_i(\omega_{i,t+1}|\theta_i)}{m_{i,t}(\omega_{i,t+1})} + \sum_{j \in N(i)} a_{ij}\mu_{j,t}(\theta_i)
+\end{equation}
 

### 2012-12-04 src/eecs598/DeGrootNode.java
Initial code commit. Some classes that we will probably need. I've only coded up their skeleton, but it should be enough to get us started.

@@ -1,0 +1,35 @@
+package eecs598;
+
+import java.util.HashMap;
+
+import edu.uci.ics.jung.graph.Graph;
+import eecs598.util.NotImplementedException;
+
+public class DeGrootNode implements Node {
+	
+	@Override
+	public void newSignal(Graph<Node, Edge> graph, double signal) {
+		// TODO Auto-generated method stub
+		//
+		// This is probably a good time to iterate over this node's neighbors
+		// and average their expected values of the parameters.
+		//
+		throw new NotImplementedException();
+		
+		
+	}
+
+	@Override
+	public HashMap<Double, Double> getBeliefs() {
+		// TODO Auto-generated method stub
+		//
+		// This is where we go from the DeGroot node's estimate of
+		// the true parameter to a distribution over possible states of 
+		// the world. We should write this in a way that makes it easy
+		// for us to change the algorithm later. Perhaps we should use a new
+		// class for that.
+		//
+		throw new NotImplementedException();
+	}
+
+}

### 2012-12-04 src/eecs598/factories/NodeFactory.java

@@ -1,0 +1,19 @@
+package eecs598.factories;
+
+import org.apache.commons.collections15.Factory;
+
+import eecs598.Node;
+import eecs598.util.NotImplementedException;
+
+public class NodeFactory implements Factory<Node> {
+
+	@Override
+	/**
+	 * Creates either a non-bayesian or a DeGroot node.
+	 */
+	public Node create() {
+		// TODO Auto-generated method stub
+		throw new NotImplementedException();
+	}
+
+}

### 2012-12-04 src/eecs598/probability/TrapezoidDistribution.java

@@ -1,0 +1,31 @@
+package eecs598.probability;
+
+import eecs598.util.NotImplementedException;
+
+/**
+ * A distribution whose pdf's support is in [0, 1] and follows a
+ * line with slope, which is the parameter, in [-2, 2].
+ * @author Pedro
+ *
+ */
+public class TrapezoidDistribution implements Distribution {
+
+	@Override
+	public double draw() {
+		// TODO Auto-generated method stub
+		throw new NotImplementedException();
+	}
+
+	@Override
+	public double pdf(double x) {
+		// TODO Auto-generated method stub
+		throw new NotImplementedException();
+	}
+
+	@Override
+	public double getParameter() {
+		// TODO Auto-generated method stub
+		throw new NotImplementedException();
+	}
+
+}

### 2012-12-04 src/eecs598/probability/ProbabilityUtil.java
Unit tests for ProbabilityUtil.

@@ -18,13 +18,17 @@ public class ProbabilityUtil {
 	 * Performs sum(probabilityMap[i].key * probabilityMap[i].value) for all valid i.
 	 * @return
 	 */
-	public double expectedValue(HashMap<Double, Double> probabilityMap) {
+	public static double expectedValue(HashMap<Double, Double> probabilityMap) {
 		// TODO write a test case.
 		double expectedValue = 0;
 		for(Map.Entry<Double, Double> valueProbPair : probabilityMap.entrySet()) {
 			double variableValue = valueProbPair.getKey();
 			double probability = valueProbPair.getValue();
-			expectedValue += variableValue * probability;
+			if(probability > 0 && probability < 1) {
+				expectedValue += variableValue * probability;
+			} else {
+				throw new IllegalArgumentException(probability + " is not a valid probability.");
+			}
 		}
 		return expectedValue;
 	}

### 2012-12-04 src/eecs598/test/ProbabilityUtilTest.java

@@ -1,0 +1,51 @@
+package eecs598.test;
+
+import static org.junit.Assert.*;
+
+import java.util.HashMap;
+
+import org.junit.Test;
+
+import eecs598.probability.ProbabilityUtil;
+
+public class ProbabilityUtilTest {
+
+	@Test
+	public void expectedValueTest() {
+		HashMap<Double, Double> probMap = new HashMap<>();
+		probMap.put(1.0, .5);
+		probMap.put(2.0, .5);
+		assertEquals(1.5, ProbabilityUtil.expectedValue(probMap), 0.0000001);
+	}
+	
+	@Test
+	public void expectedValueTest2() {
+		HashMap<Double, Double> probMap = new HashMap<>();
+		probMap.put(0.0, .5);
+		probMap.put(0.0, .5);
+		assertEquals(0, ProbabilityUtil.expectedValue(probMap), 0.0000001);
+	}
+	
+	@Test
+	public void expectedValueTest3() {
+		HashMap<Double, Double> probMap = new HashMap<>();
+		probMap.put(1.0, -.5);
+		probMap.put(2.0, .5);
+		try {
+			ProbabilityUtil.expectedValue(probMap);
+			fail();
+		} catch(IllegalArgumentException e) {}
+	}
+
+	@Test
+	public void expectedValueTest4() {
+		HashMap<Double, Double> probMap = new HashMap<>();
+		probMap.put(1.0, 1.5);
+		probMap.put(2.0, .5);
+		try {
+			ProbabilityUtil.expectedValue(probMap);
+			fail();
+		} catch(IllegalArgumentException e) {}
+	}
+
+}

### 2012-12-04 docs/paper.tex
Moved report to docs directory
Added some references
Wrote up much of the model.  Working on conversion of DeGroot to Non-Bayesian belief states.

--- 2012-12-03 paper.tex
@@
 \title{Mixed Non-Bayesian and DeGroot Learning}
-\author{Pedro Barbuda\\pdaquino@umich.edu \and Dan Clark\\ddclark@umich.edu}
+\author{Pedro d'Aquino\\pdaquino@umich.edu \and Dan Clark\\ddclark@umich.edu}
 \date{December 11, 2012}
@@
 \section{Introduction}
+
+\cite{Jadbabaie2012}
+\cite{DeGroot1974}
 
@@
 \begin{equation}
-P^*(x)=\begin{cases}
-m^* \cdot x & 0 \le x \le 1 \\
+p^*(x)=\begin{cases}
+m^* \cdot x + \frac{1}{2}(2-m^*) & 0 \le x \le 1 \\
 0, & \text{otherwise}
@@
 The slope $\{ m^* \in \mathbf{R} : -2 \le m^* \le 2 \}$ will be the defining characteristic of the distribution.
-We have chosen to bound $m^*$ between -2 and 2 so that the support of $P_t$  is always over $[0,1]$.
+We have chosen to bound $m^*$ between -2 and 2 add the term $\frac{1}{2}(2-m^*)$ so that the support of $p^*(x)$  is always over $[0,1]$.
 The value of the parameter $m^*$ is the ``true'' state that each node is trying to learn.
 
-At each timestep $t$, every Non-Bayesian node $i$ will receive a signal $s_{i,t}$ which is a value drawn from $P_t$.
+At each timestep $t$, every Non-Bayesian node $i$ will receive a signal $s_{i,t}$ which is a value drawn from $p^*(x)$.
 These observations will be used by the nodes in the network to construct a belief about $m^*$.
@@
 Let $\Theta = \{\theta_0, \theta_1,...\theta_n\}, n < \infty$ be the discrete set of possible states of the world over which each Non-Bayesian node holds a distribution of belief.
-Each $\theta_i$ corresponds to the belief that the slope of $P^*$ is
-\begin{equation} \label{eq:theta_meaning}
-m^* = \frac{4i}{n - 1} - 2
+Each $\theta_i$ corresponds to the belief that the slope of $p^*(x)$ is equal to $m_i$ where
+\begin{equation}
+\label{eq:theta_meaning}
+m_i = \frac{4i}{n - 1} - 2
 \end{equation}
@@
 That is, a DeGroot node's $i$'s belief of the true slope value $m^*$ is given at time $t+1$ as
-\begin{equation} \label{eq:degroot_update}
+\begin{equation}
+\label{eq:degroot_update}
 m_{i,t+1} = \sum_{j \in N(i)} a_{ij}m_{j,t}
@@
 
-When a DeGroot node a Non-Bayesian neighbor performs an update it must obtain a value 
-$m_{j,t}$ for the belief of this node.  This is calculated as
+When a DeGroot node with a Non-Bayesian neighbor performs an update it must obtain a value 
+$m_{j,t}^\prime$ for the belief of this neighbor.  This is calculated as
 
 \begin{equation}
-m_{j,t} = \sum_{k=1}^n\mu_{j,t}(\theta_k)(\frac{4i}{n - 1} - 2)
+m_{j,t}^\prime = \sum_{k=1}^n\mu_{j,t}(\theta_k)(\frac{4i}{n - 1} - 2)
 \end{equation}
 
-Here we are taking a weighted average of the $m^*$ value represented by each state $\theta_i$ as defined in equation \ref{eq:theta_meaning}, where the weights are given by $j$'s level of belief in each state.
+Here we are taking a weighted average of the $m^*$ value represented by each state $\theta_i$ as defined in equation~\ref{eq:theta_meaning}, where the weights are given by $j$'s level of belief in each state.
 
@@
 The update of a Non-Bayesian node in our model is handled similarly to the method laid out 
-in Jadbabaie et. al. % @todo[DDC] Figure out references system
-
-% [DDC] Just putting in the equations for the moment.
+in \cite{Jadbabaie2012}.  We denote the belief of a node $i$ that it will receive the signal $s_i$ at time $t$ as $m_{i,t}(s_i)$, defined as follows:
 
@@
 
+% @todo[DDC] More detail for derivation/explanation of likelihood?
+In this case the likelihood function $\ell_i(s_i|\theta_i)$ can be obtained from the probability distribution function represented by the belief state $\theta_i$.
+
+\begin{equation}
+\label{eq:likelihood}
+\ell_i(s_i|\theta_i) = m_i s_i + \frac{1}{2}(2 - m_i)
+\end{equation}
+where $m_i$ is defined as in equation~\ref{eq:theta_meaning}.
+
+The update of a node's belief in each state $\theta_i$ for a given time period $t$ is then given by
+
 \begin{equation}
@@
 
+Here the first term is the Bayesian update of the belief $\mu_{i,t}(\theta_i)$ after observing the signal $\omega_{i,t+1}$ multiplied by the node's self reliance $a_{ii}$.
+The summation is the linear incorporation of the beilefs of $i$'s neighbors.
+
+This update differs from the previous work in two major ways.
+Firstly, we provide each Non-Bayesian node with only a single signal per timestep, where this signal is a single draw from the probability distribution $p^*(x)$.
+
+Secondly, we must define $\mu_{j,t}(\theta_i)$ when $j$ is a DeGroot node.
+We consider two methods for doing so, defined in sections \ref{sec:draw_from_degroot} and \ref{sec:likelihood_metric} respectively.
+
+\subsubsection{Belief Distribution from Draw of Probability Distribution}
+\label{sec:draw_from_degroot}
+
+The first method that we consider for converting a DeGroot node $j$'s belief to a prior which can be included in a Non-Bayesian node $i$'s belief update involves generating a probability distribution from the $j$'s current belief and drawing from this distribution.
+For each DeGroot neighbor of $i$ at time $t$ we define the probability distribution
+\begin{equation}
+p_{j,t}(x)=\begin{cases}
+m_{j,t} x + \frac{1}{2}(2-m^*) & 0 \le x \le 1 \\
+0, & \text{otherwise}
+\end{cases}
+\end{equation}
+
+This is simply the distribution which $j$ believes to be the state of the world.
+We then draw a single signal $s_{j,t}^\prime$ from this distribution.
+We create a belief distribution $\mu_{j,t}^\prime$ from $s_{j,t}^\prime$ by performing a Bayesian-style update with equal priors.
+
+\begin{equation}
+\mu_{j,t}^\prime(\theta_i) = \frac{\ell_i(s_{j,t}^\prime|\theta_i)}{m_{i,t}(s_{j,t}^\prime)}
+\end{equation}
+
+This generated belief distribution $\mu_{j,t}^\prime$ is then used as
+
+% @todo[DDC] Still working on this section
+
+\subsubsection{Belief Distribution from Likelihood Distance Metric}
+\label{sec:likelihood_metric}
+
+\bibliographystyle{plain}
+\bibliography{eecs598Report}
+
 \end{document}

### 2012-12-05 src/eecs598/DeGrootNode.java
Implementation and unit tests of NonBayesianNode.

@@ -1,14 +1,17 @@
 package eecs598;
 
+import java.util.Collection;
 import java.util.HashMap;
+import java.util.List;
 
 import edu.uci.ics.jung.graph.Graph;
+import eecs598.probability.Distribution;
 import eecs598.util.NotImplementedException;
 
 public class DeGrootNode implements Node {
 	
 	@Override
-	public void newSignal(Graph<Node, Edge> graph, double signal) {
+	public void newSignal(Collection<Node> neighbors, double signal) {
 		// TODO Auto-generated method stub
 		//
 		// This is probably a good time to iterate over this node's neighbors
@@ -29,6 +32,12 @@ public class DeGrootNode implements Node {
 		// for us to change the algorithm later. Perhaps we should use a new
 		// class for that.
 		//
+		throw new NotImplementedException();
+	}
+
+	@Override
+	public void setPossibleDistributions(List<Distribution> distributions) {
+		// TODO Auto-generated method stub
 		throw new NotImplementedException();
 	}
 

### 2012-12-05 src/eecs598/Node.java

@@ -1,8 +1,10 @@
 package eecs598;
 
+import java.util.Collection;
 import java.util.HashMap;
+import java.util.List;
 
-import edu.uci.ics.jung.graph.Graph;
+import eecs598.probability.Distribution;
 
 public interface Node {
 	
@@ -11,11 +13,17 @@ public interface Node {
 	 * We pass the graph in case nodes want to use information from neighbors.
 	 * @param signal
 	 */
-	public void newSignal(Graph<Node, Edge> graph, double signal);
+	public void newSignal(Collection<Node> neighbors, double signal);
 	
 	/**
 	 * Returns the node's current set of beliefs on possible states.
 	 * @return
 	 */
 	public HashMap<Double, Double> getBeliefs();
+	
+	/**
+	 * Sets the list of possible distributions.
+	 * @param distributions
+	 */
+	public void setPossibleDistributions(List<Distribution> distributions);
 }

### 2012-12-05 src/eecs598/NonBayesianNode.java

@@ -1,9 +1,13 @@
 package eecs598;
 
+import java.util.ArrayList;
+import java.util.Collection;
 import java.util.HashMap;
+import java.util.List;
+import java.util.Map;
 
-import edu.uci.ics.jung.graph.Graph;
-import eecs598.util.NotImplementedException;
+import eecs598.probability.Distribution;
+import eecs598.probability.ProbabilityUtil;
 
 public class NonBayesianNode implements Node {
 
@@ -13,29 +17,166 @@ public class NonBayesianNode implements Node {
 	 */
 	private HashMap<Double, Double> beliefs;
 	
-	//
-	// When NB nodes are constructed, we need to pass it
-	// all the possible Distributions, and then we extract the
-	// possible parameters and put them in the beliefs map with
-	// a uniform prior.
-	//
+	/**
+	 * An order list of possible distributions.
+	 */
+	private List<Distribution> distributions;
+	
+	private int id;
+	
+	public NonBayesianNode(int id, List<Distribution> possibleDistributions) {
+		this.id = id;
+		setPossibleDistributions(possibleDistributions);
+	}
 	
 	@Override
-	public void newSignal(Graph<Node, Edge> graph, double signal) {
-		// TODO Auto-generated method stub
+	public void newSignal(Collection<Node> neighbors, double signal) {
 		//
 		// Perform the bayesian update + the degroot-style averaging of neighbors.
 		//
-		throw new NotImplementedException();
+		doBayesianUpdate(neighbors, signal);
+		ProbabilityUtil.normalizeToOne(beliefs);
+		doNonBayesianUpdate(neighbors, signal);
+		ProbabilityUtil.normalizeToOne(beliefs);
+	}
+	
+	protected void doBayesianUpdate(Collection<Node> neighbors, double signal) {
+		//
+		// Let w be the signal and T a distribution that might have generated w.
+		//
+		// P(T | w) = (P(w | T)/P(w))P(T)
+		//
+		// The first term is proportional to the pdf of T. The second is the prior,
+		// currently in the beliefs map. We have to normalize the pdfs in order to
+		// get P(w|T)/P(W).
+		//
+		
+		//
+		// Get p(w|T)/p(w).
+		//
+		List<Double> pdfsAtW = new ArrayList<Double>(distributions.size());
+		for(Distribution dist : distributions) {
+			double pdf = dist.pdf(signal); 
+			pdfsAtW.add(pdf);
+		}
+		
[…]

### 2012-12-05 src/eecs598/probability/ProbabilityUtil.java

@@ -1,9 +1,10 @@
 package eecs598.probability;
 
+import java.util.ArrayList;
+import java.util.Collection;
 import java.util.HashMap;
+import java.util.List;
 import java.util.Map;
-
-import eecs598.util.NotImplementedException;
 
 /**
  * Helper class for simple probability methods like getting the expected value.
@@ -31,5 +32,37 @@ public class ProbabilityUtil {
 			}
 		}
 		return expectedValue;
+	}
+	
+	/**
+	 * Normalizes a list of values such that their sum adds up to one.
+	 * @return the list of normalized values.
+	 */
+	public static List<Double> normalizeToOne(List<Double> values) {
+		double sum = sum(values);
+		List<Double> normalizedValues = new ArrayList<Double>(values.size());
+		for(Double value : values) {
+			normalizedValues.add(value / sum);
+		}
+		return normalizedValues;
+	}
+	
+	/**
+	 * Normalizes a list of values such that their sum adds up to one.
+	 * @return the list of normalized values.
+	 */
+	public static void normalizeToOne(HashMap<? extends Object, Double> values) {
+		double sum = sum(values.values());
+		for(Map.Entry<? extends Object, Double> entry : values.entrySet()) {
+			entry.setValue(entry.getValue() / sum);
+		}
+	}
+	
+	private static double sum(Collection<Double> values) {
+		double sum = 0.0;
+		for(Double value : values) {
+			sum += value;
+		}
+		return sum;
 	}
 }

### 2012-12-05 src/eecs598/test/NonBayesianNodeTest.java

@@ -1,0 +1,180 @@
+package eecs598.test;
+
+import static org.junit.Assert.*;
+
+import java.util.ArrayList;
+import java.util.Collection;
+import java.util.List;
+
+import org.junit.Test;
+
+import edu.uci.ics.jung.graph.Graph;
+import eecs598.Edge;
+import eecs598.Node;
+import eecs598.NonBayesianNode;
+import eecs598.probability.Distribution;
+
+public class NonBayesianNodeTest extends NonBayesianNode {
+
+	public NonBayesianNodeTest() { super(0, new ArrayList<Distribution>()); }
+
+	@Test
+	public void testSingleNodeConvergence() {
+		//
+		// Simplest test possible: one node with a signal s.t. it can tell the right
+		// distribution with 100% likelihood. We use a distribution called ZeroPdf whose
+		// pdf always returns 0 to simulate this.
+		//
+		Distribution uniform = new TestDistributions.Uniform(1);
+		Distribution zero = new TestDistributions.ZeroPdf(0);
+		
+		List<Distribution> distributions = new ArrayList<Distribution>();
+		distributions.add(uniform); distributions.add(zero);
+		
+		NonBayesianNode node = new NonBayesianNode(1, distributions);
+		
+		node.newSignal(new ArrayList<Node>(), 0.2);
+		
+		assertEquals(node.getBeliefs().get(uniform.getParameter()), 1.0, 0.0001);
+	}
+	
+	@Test
+	public void testSingleNodeUniform() {
+		Distribution uniform1 = new TestDistributions.Uniform(1);
+		Distribution uniform2 = new TestDistributions.Uniform(2);
+		
+		List<Distribution> distributions = new ArrayList<Distribution>();
+		distributions.add(uniform1); distributions.add(uniform2);
+		
+		NonBayesianNode node = new NonBayesianNode(1, distributions);
+		
+		node.newSignal(new ArrayList<Node>(), 0.2);
+		
+		assertEquals(0.5, node.getBeliefs().get(uniform1.getParameter()), 0.0001);
+		assertEquals(0.5, node.getBeliefs().get(uniform2.getParameter()), 0.0001);
+	}
+	
+	@Test
+	public void testTwoNodes() {
+		//
+		// Two nodes, A and B. A sees two uniform distributions. B sees a uniform
[…]

### 2012-12-05 src/eecs598/test/TestDistributions.java

@@ -1,0 +1,56 @@
+package eecs598.test;
+
+import eecs598.probability.Distribution;
+import eecs598.util.NotImplementedException;
+
+public class TestDistributions {
+	public static class Uniform implements Distribution {
+		private int id;
+		
+		public Uniform(int id) {
+			super();
+			this.id = id;
+		}
+
+		@Override
+		public double draw() {
+			throw new NotImplementedException();
+		}
+
+		@Override
+		public double pdf(double x) {
+			return 1;
+		}
+
+		@Override
+		public double getParameter() {
+			return id;
+		}
+	}
+	
+	public static class ZeroPdf implements Distribution {
+		private int id;
+
+		
+		public ZeroPdf(int id) {
+			super();
+			this.id = id;
+		}
+
+		@Override
+		public double draw() {
+			throw new IllegalArgumentException();
+		}
+
+		@Override
+		public double pdf(double x) {
+			return 0;
+		}
+
+		@Override
+		public double getParameter() {
+			return id;
+		}
+		
+	}
+}

### 2012-12-05 src/eecs598/test/TestGraphs.java

@@ -1,0 +1,46 @@
+package eecs598.test;
+
+import java.util.ArrayList;
+
+import org.apache.commons.collections15.Factory;
+
+import edu.uci.ics.jung.algorithms.generators.random.KleinbergSmallWorldGenerator;
+import edu.uci.ics.jung.graph.Graph;
+import edu.uci.ics.jung.graph.SparseGraph;
+import eecs598.Edge;
+import eecs598.Node;
+import eecs598.NonBayesianNode;
+import eecs598.probability.Distribution;
+
+public class TestGraphs {
+	public static class NonBayesianFactory implements Factory<Node> {
+		int id = 1;
+		@Override
+		public Node create() {
+			return new NonBayesianNode(id++, new ArrayList<Distribution>());
+		}
+	}
+	
+	public static class EdgeFactory implements Factory<Edge> {
+		int id = 1;
+		@Override
+		public Edge create() {
+			return new Edge(id++);
+		}
+	}
+	
+	public static class GraphFactory implements Factory<Graph<Node, Edge>> {
+
+		@Override
+		public Graph<Node, Edge> create() {
+			return new SparseGraph<Node, Edge>();
+		}
+	}
+	
+	public static Graph<Node, Edge> smallWorldNonBayesian(int latticeSize) {
+		KleinbergSmallWorldGenerator<Node, Edge> kleinbergGenerator = new KleinbergSmallWorldGenerator<>(
+				new GraphFactory(), new NonBayesianFactory(), new EdgeFactory(), latticeSize, 5);
+		
+		return kleinbergGenerator.create();
+	}
+}

### 2012-12-05 src/eecs598/BeliefEstimator.java
DeGroot nodes implemented, with the random draw method for belief estimation and not taking signals into account.

@@ -1,0 +1,14 @@
+package eecs598;
+import java.util.HashMap;
+import java.util.List;
+
+import eecs598.probability.*;
+/**
+ * This interface specifies objects that are able to convert a DeGroot style parameter
+ * approximation into a set of beliefs over the set of possible probability distributions.
+ * @author Pedro
+ *
+ */
+public interface BeliefEstimator {
+	public HashMap<Double, Double> estimateBeliefs(double parameterEstimate, List<Distribution> possibleDistributions);
+}

### 2012-12-05 src/eecs598/DeGrootNode.java

@@ -4,41 +4,119 @@ import java.util.Collection;
 import java.util.HashMap;
 import java.util.List;
 
-import edu.uci.ics.jung.graph.Graph;
 import eecs598.probability.Distribution;
-import eecs598.util.NotImplementedException;
+import eecs598.probability.ProbabilityUtil;
 
+/**
+ * Represents a DeGroot node, which maintains an estimate of the parameter. The main
+ * mechanism through which it achieves that is using its neighbors information.
+ * 
+ * This class requires two objects to work. One of them is responsible for incorporating
+ * a signal into the current estimate. The other class converts the parameter
+ * estimate into a probability distribution over the possible underlying distributions.
+ * 
+ * @author Pedro
+ *
+ */
 public class DeGrootNode implements Node {
 	
-	@Override
-	public void newSignal(Collection<Node> neighbors, double signal) {
-		// TODO Auto-generated method stub
-		//
-		// This is probably a good time to iterate over this node's neighbors
-		// and average their expected values of the parameters.
-		//
-		throw new NotImplementedException();
-		
-		
+	// TODO I am not considering the node's own estimate for the first time
+	// it receives a signal -- I am just copying the average of the neighbor's.
+	// Does it make sense? 
+	private double estimate = 0.0;
+	private boolean firstSignal = true;
+	
+	/**
+	 * Given a signal, updates the current estimate.
+	 */
+	private ParameterEstimator parameterEstimator;
+	
+	/**
+	 * Converts the estimate into a set of beliefs, i.e. a probability
+	 * distribution.
+	 */
+	private BeliefEstimator beliefEstimator;
+	
+	/**
+	 * We use this only to estimate the beliefs.
+	 */
+	private List<Distribution> possibleDistributions;
+	
+	public DeGrootNode(ParameterEstimator parameterEstimator,
+			BeliefEstimator beliefEstimator) {
+		super();
+		this.parameterEstimator = parameterEstimator;
+		this.beliefEstimator = beliefEstimator;
 	}
 
 	@Override
+	public void newSignal(Collection<Node> neighbors, double signal) {
+		//
+		// Use the signal to update our estimate.
+		//
+		estimate = parameterEstimator.estimateParameter(signal, estimate);
+
+		//
+		// Average the neighbors' beliefs, with weights.
+		//
+		double sumEstimates = 0.0;
+		double sumWeights = 0.0;
+		
+		//
[…]

### 2012-12-05 src/eecs598/NopParameterEstimator.java

@@ -1,0 +1,15 @@
+package eecs598;
+
+/**
+ * This class doesn't do anything with the new signal.
+ * @author Pedro
+ *
+ */
+public class NopParameterEstimator implements ParameterEstimator {
+
+	@Override
+	public double estimateParameter(double signal, double currentEstimate) {
+		return currentEstimate;
+	}
+
+}

### 2012-12-05 src/eecs598/ParameterEstimator.java

@@ -1,0 +1,11 @@
+package eecs598;
+
+public interface ParameterEstimator {
+	/**
+	 * Return a new estimate of the parameter after receiving a signal.
+	 * @param signal
+	 * @param currentEstimate
+	 * @return
+	 */
+	public double estimateParameter(double signal, double currentEstimate);
+}

### 2012-12-05 src/eecs598/RandomDrawBeliefEstimator.java

@@ -1,0 +1,58 @@
+package eecs598;
+
+import java.util.HashMap;
+import java.util.List;
+
+import eecs598.probability.Distribution;
+import eecs598.probability.DistributionFactory;
+import eecs598.probability.ProbabilityUtil;
+
+/**
+ * Estimates the beliefs by constructing a distribution that
+ * matches the esimated parameter, sampling from it and then
+ * seeing how likely that sample was to have come from the candidate
+ * distributions.
+ * 
+ * @author Pedro
+ *
+ */
+public class RandomDrawBeliefEstimator implements BeliefEstimator {
+	
+	/**
+	 * This class creates parametrized distributions. We use it to construct
+	 * a customized distribution with our current estimate of the parameter.
+	 */
+	private DistributionFactory distributionFactory;
+	
+	public RandomDrawBeliefEstimator(DistributionFactory distributionFactory) {
+		super();
+		this.distributionFactory = distributionFactory;
+	}
+	@Override
+	public HashMap<Double, Double> estimateBeliefs(double parameterEstimate,
+			List<Distribution> possibleDistributions) {
+		//
+		// We estimate the beliefs using the following process. We first construct
+		// a distribution whose parameter is our current estimate; we then draw from
+		// this distribution. The belief of a possible distribution is the
+		// likelihood of this random sample having originated from that distribution,
+		// which is a value proportional to that distribution's pdf.
+		//
+		HashMap<Double, Double> beliefs = new HashMap<>(possibleDistributions.size());
+		
+		// TODO try sampling many times and averaging them out?
+		
+		Distribution estimatedDistribution = distributionFactory.create(parameterEstimate);
+		
+		double randomSample = estimatedDistribution.draw();
+		for(Distribution candidate : possibleDistributions) {
+			double pdf = candidate.pdf(randomSample);
+			beliefs.put(candidate.getParameter(), pdf);
+		}
+		
+		ProbabilityUtil.normalizeToOne(beliefs);
+		
+		return beliefs;
+	}
+
+}

### 2012-12-05 src/eecs598/probability/DistributionFactory.java

@@ -1,0 +1,5 @@
+package eecs598.probability;
+
+public interface DistributionFactory {
+	public Distribution create(double parameter);
+}

### 2012-12-05 src/eecs598/probability/ProbabilityUtil.java

@@ -20,12 +20,11 @@ public class ProbabilityUtil {
 	 * @return
 	 */
 	public static double expectedValue(HashMap<Double, Double> probabilityMap) {
-		// TODO write a test case.
 		double expectedValue = 0;
 		for(Map.Entry<Double, Double> valueProbPair : probabilityMap.entrySet()) {
 			double variableValue = valueProbPair.getKey();
 			double probability = valueProbPair.getValue();
-			if(probability > 0 && probability < 1) {
+			if(probability >= 0 && probability <= 1) {
 				expectedValue += variableValue * probability;
 			} else {
 				throw new IllegalArgumentException(probability + " is not a valid probability.");

### 2012-12-05 src/eecs598/probability/TrapezoidDistribution.java

@@ -9,6 +9,13 @@ import eecs598.util.NotImplementedException;
  *
  */
 public class TrapezoidDistribution implements Distribution {
+	
+	private double m = 0.0;
+	
+	public TrapezoidDistribution(double m) {
+		super();
+		this.m = m;
+	}
 
 	@Override
 	public double draw() {
@@ -24,8 +31,7 @@ public class TrapezoidDistribution implements Distribution {
 
 	@Override
 	public double getParameter() {
-		// TODO Auto-generated method stub
-		throw new NotImplementedException();
+		return m;
 	}
 
 }

### 2012-12-05 src/eecs598/probability/TrapezoidFactory.java

@@ -1,0 +1,10 @@
+package eecs598.probability;
+
+public class TrapezoidFactory implements DistributionFactory {
+
+	@Override
+	public Distribution create(double parameter) {
+		return new TrapezoidDistribution(parameter);
+	}
+
+}

### 2012-12-05 src/eecs598/test/DeGrootNodeTest.java

@@ -1,0 +1,48 @@
+package eecs598.test;
+
+import static org.junit.Assert.*;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import org.junit.Test;
+
+import eecs598.DeGrootNode;
+import eecs598.Node;
+import eecs598.NopParameterEstimator;
+import eecs598.RandomDrawBeliefEstimator;
+import eecs598.test.helpers.ExpectedValueNode;
+import eecs598.test.helpers.TestDistributions;
+
+public class DeGrootNodeTest {
+
+	@Test
+	public void testOneNeighbor() {
+		ExpectedValueNode neighbor = new ExpectedValueNode(42.0);
+		DeGrootNode node = new DeGrootNode(new NopParameterEstimator(),
+				new RandomDrawBeliefEstimator(new TestDistributions.UniformFactory()));
+		
+		List<Node> nodeNeighbors = new ArrayList<Node>();
+		nodeNeighbors.add(neighbor);
+		
+		node.newSignal(nodeNeighbors, 0.0);
+		
+		assertEquals(42.0, node.getParameterEstimate(), 0.0001);
+	}
+	
+	@Test
+	public void testTwoNeighbors() {
+		ExpectedValueNode neighbor1 = new ExpectedValueNode(42.0);
+		ExpectedValueNode neighbor2 = new ExpectedValueNode(0);
+		DeGrootNode node = new DeGrootNode(new NopParameterEstimator(),
+				new RandomDrawBeliefEstimator(new TestDistributions.UniformFactory()));
+		
+		List<Node> nodeNeighbors = new ArrayList<Node>();
+		nodeNeighbors.add(neighbor1); nodeNeighbors.add(neighbor2);
+		
+		node.newSignal(nodeNeighbors, 0.0);
+		
+		assertEquals(21.0, node.getParameterEstimate(), 0.0001);
+	}
+
+}

### 2012-12-05 src/eecs598/test/NonBayesianNodeTest.java

@@ -13,6 +13,8 @@ import eecs598.Edge;
 import eecs598.Node;
 import eecs598.NonBayesianNode;
 import eecs598.probability.Distribution;
+import eecs598.test.helpers.TestDistributions;
+import eecs598.test.helpers.TestGraphs;
 
 public class NonBayesianNodeTest extends NonBayesianNode {
 

### 2012-12-05 src/eecs598/test/RandomDrawBeliefEstimatorTest.java

@@ -1,0 +1,50 @@
+package eecs598.test;
+
+import static org.junit.Assert.*;
+
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.List;
+
+import org.junit.Test;
+
+import eecs598.RandomDrawBeliefEstimator;
+import eecs598.probability.Distribution;
+import eecs598.probability.DistributionFactory;
+import eecs598.test.helpers.TestDistributions;
+
+public class RandomDrawBeliefEstimatorTest {
+
+	@Test
+	public void testUniform() {
+		//
+		// Creates a bunch of uniform distributions and checks
+		// whether they end up being as likely.
+		//
+		
+		int countPossibleDistributions = 10;
+		
+		//
+		// The parameter doesn't matter for the uniform distribution.
+		//
+		
+		DistributionFactory factory = new TestDistributions.UniformFactory(); 
+		RandomDrawBeliefEstimator estimator = new RandomDrawBeliefEstimator(factory);
+		
+		List<Distribution> possibleDistributions = new ArrayList<Distribution>();
+		for(int i = 0; i < countPossibleDistributions; i++) {
+			possibleDistributions.add(factory.create(0.0));
+		}
+		
+		HashMap<Double, Double> beliefs = estimator.estimateBeliefs(0.5, possibleDistributions);
+		double expectedBelief = 1.0 / countPossibleDistributions;
+		
+		for(Double belief : beliefs.values()) {
+			assertEquals(expectedBelief, belief, 0.0001);
+		}
+		
+		
+		
+	}
+
+}

### 2012-12-05 src/eecs598/test/helpers/ExpectedValueNode.java

@@ -1,0 +1,44 @@
+package eecs598.test.helpers;
+
+import java.util.Collection;
+import java.util.HashMap;
+import java.util.List;
+
+import eecs598.Node;
+import eecs598.probability.Distribution;
+
+/**
+ * A node that returns a set of beliefs such that the expected
+ * parameter value is a user-specified value.
+ * @author Pedro
+ *
+ */
+public class ExpectedValueNode implements Node {
+	private double expectedValue = 0;
+	public ExpectedValueNode(double expectedBeliefValue) {
+		this.expectedValue = expectedBeliefValue;
+	}
+	
+	@Override
+	public void newSignal(Collection<Node> neighbors, double signal) {
+	}
+
+	/**
+	 * Returns a probability distribution whose expected value is expectedValue.
+	 * No other guarantee is made about it; in special it does not follow
+	 * whatever might be passed in setPossibleDistributions.
+	 * @return
+	 */
+	@Override
+	public HashMap<Double, Double> getBeliefs() {
+		HashMap<Double, Double> beliefs = new HashMap<>();
+		beliefs.put(expectedValue, 1.0);
+		return beliefs;
+	}
+
+	@Override
+	public void setPossibleDistributions(List<Distribution> distributions) {
+
+	}
+
+}

### 2012-12-05 src/eecs598/test/helpers/TestDistributions.java

@@ -1,12 +1,15 @@
-package eecs598.test;
+package eecs598.test.helpers;
+
+import java.util.Random;
 
 import eecs598.probability.Distribution;
+import eecs598.probability.DistributionFactory;
 import eecs598.util.NotImplementedException;
 
 public class TestDistributions {
 	public static class Uniform implements Distribution {
 		private int id;
-		
+		private Random random = new Random();
 		public Uniform(int id) {
 			super();
 			this.id = id;
@@ -14,7 +17,7 @@ public class TestDistributions {
 
 		@Override
 		public double draw() {
-			throw new NotImplementedException();
+			return random.nextDouble();
 		}
 
 		@Override
@@ -52,5 +55,12 @@ public class TestDistributions {
 			return id;
 		}
 		
+	}
+	
+	public static class UniformFactory implements DistributionFactory {
+		private int id = 1;
+		public Distribution create(double parameter) {
+			return new Uniform(id++);
+		}
 	}
 }

### 2012-12-05 src/eecs598/test/helpers/TestGraphs.java

@@ -1,4 +1,4 @@
-package eecs598.test;
+package eecs598.test.helpers;
 
 import java.util.ArrayList;
 

### 2012-12-05 docs/paper.tex
Mostly finished with first draft of model write-up

@@
 \end{equation}
+
+% @todo[DDC] Graph/figure of this would probably be good to have.
+
 The slope $\{ m^* \in \mathbf{R} : -2 \le m^* \le 2 \}$ will be the defining characteristic of the distribution.
-We have chosen to bound $m^*$ between -2 and 2 add the term $\frac{1}{2}(2-m^*)$ so that the support of $p^*(x)$  is always over $[0,1]$.
+We have chosen to bound $m^*$ between -2 and 2 and add the term $\frac{1}{2}(2-m^*)$ so that the support of $p^*(x)$  is always over $[0,1]$.
 The value of the parameter $m^*$ is the ``true'' state that each node is trying to learn.
@@
 
-The foremost difficulty in combining the Non-Bayesian and DeGroot models is that belief of Non-Bayesian nodes is a probability distribution over a finite set of possible states of the world.
-
-For a DeGroot node $i$, we represent the belief state of $i$ at time t as a single value 
+For a DeGroot node $i$, we represent the belief state of $i$ at time $t$ as a single value 
 $m_{i,t} \in \mathbf{R}$.
-
-Therefore it is necessary to develop a conversion between the belief states of Non-Bayesian and DeGroot nodes.
+However, belief of Non-Bayesian nodes is a probability distribution over a finite set of possible states of the world.
+There is thus a tension between these two schemes and it is necessary to develop a conversion between the belief states of Non-Bayesian and DeGroot nodes.
 
@@
 
-To represent a belief about the continuous slope value $m*$ for a Non-Bayesian node we discretize $m$ in the following manner.
+To represent a belief about the continuous slope value $m^*$ for a Non-Bayesian node we discretize $m$ in the following manner.
 Let $\Theta = \{\theta_0, \theta_1,...\theta_n\}, n < \infty$ be the discrete set of possible states of the world over which each Non-Bayesian node holds a distribution of belief.
-Each $\theta_i$ corresponds to the belief that the slope of $p^*(x)$ is equal to $m_i$ where
+Each $\theta_k$ corresponds to the belief that the slope of $p^*(x)$ is equal to $m_k$ where
 \begin{equation}
 \label{eq:theta_meaning}
-m_i = \frac{4i}{n - 1} - 2
+\hat{m_k} = \frac{4k}{n - k} - 2
 \end{equation}
@@
 \end{equation}
-For each Non-Bayesian node $i$, the belief at time $t$ that $\theta_i$ is the true state of the world is denoted by $\mu_{i,t}(\theta_i)$.
+For each Non-Bayesian node $i$, the belief at time $t$ that $\theta_k$ is the true state of the world is denoted by $\mu_{i,t}(\theta_k)$.
 Thus $\{ \mu_{i,t}(\theta_1), \mu_{i,t}(\theta_2), ...
@@
 
-\subsection{Updating DeGroot Belief}
+\subsection{Learning in DeGroot Nodes}
 DeGroot nodes in our model do not directly receive signals; they act merely as message-passers in the network.
@@
 \end{equation}
-for all DeGroot nodes $i$.  Thus the DeGroot update in equation \ref{eq:degroot_update} is simply a weighted average of its neighbors beliefs in the previous timestep.
+for all DeGroot nodes $i$.  Thus the DeGroot update in equation \ref{eq:degroot_update} is simply a weighted average of its neighbors' beliefs in the previous timestep.
 
@@
 \begin{equation}
-m_{j,t}^\prime = \sum_{k=1}^n\mu_{j,t}(\theta_k)(\frac{4i}{n - 1} - 2)
+m_{j,t}^\prime = \sum_{k=1}^n\mu_{j,t}(\theta_k)\hat{m_k}
 \end{equation}
 
-Here we are taking a weighted average of the $m^*$ value represented by each state $\theta_i$ as defined in equation~\ref{eq:theta_meaning}, where the weights are given by $j$'s level of belief in each state.
+Here we are taking a weighted average of the $\hat{m_k}$ slope values represented by each state $\theta_k$ as defined in equation~\ref{eq:theta_meaning}, where the weights are given by $j$'s level of belief in each state.
 
-\subsection{Updating Non-Bayesian Belief}
+\subsection{Learning in Non-Bayesian Nodes}
 
@@
 \begin{equation}
-m_{i,t}(s_i) = \int_\Theta \ell_i(s_i|\theta)d\mu_{i,t}(\theta) = \sum_{i=1}^n \ell_i(s_i|\theta_i)\mu_{i,t}(\theta_i)
+m_{i,t}(s_i) = \int_\Theta \ell_i(s_i|\theta)d\mu_{i,t}(\theta) = \sum_{k=1}^n \ell_i(s_i|\theta_k)\mu_{i,t}(\theta_k)
 \end{equation}
@@
 % @todo[DDC] More detail for derivation/explanation of likelihood?
-In this case the likelihood function $\ell_i(s_i|\theta_i)$ can be obtained from the probability distribution function represented by the belief state $\theta_i$.
+In this case the likelihood function $\ell_i(s_i|\theta_k)$ can be obtained from the probability distribution function represented by the belief state $\theta_k$.
 
@@
 \label{eq:likelihood}
-\ell_i(s_i|\theta_i) = m_i s_i + \frac{1}{2}(2 - m_i)
+\ell_i(s_i|\theta_k) = \hat{m_k} s_i + \frac{1}{2}(2 - \hat{m_k})
 \end{equation}
-where $m_i$ is defined as in equation~\ref{eq:theta_meaning}.
+where $\hat{m_k}$ is defined as in equation~\ref{eq:theta_meaning}.
 
-The update of a node's belief in each state $\theta_i$ for a given time period $t$ is then given by
+The update of a node's belief in each state $\theta_k$ for a given time period $t$ is then given by
 
 \begin{equation}
-\mu_{i,t+1}(\theta_i) = a_{ii}\mu_{i,t}(\theta_i)\frac{\ell_i(\omega_{i,t+1}|\theta_i)}{m_{i,t}(\omega_{i,t+1})} + \sum_{j \in N(i)} a_{ij}\mu_{j,t}(\theta_i)
+\label{eq:non_bayesian_update}
+\mu_{i,t+1}(\theta_k) = a_{ii}\mu_{i,t}(\theta_k)\frac{\ell_i(\omega_{i,t+1}|\theta_k)}{m_{i,t}(\omega_{i,t+1})} + \sum_{j \in N(i)} a_{ij}\mu_{j,t}(\theta_k)
 \end{equation}
 
-Here the first term is the Bayesian update of the belief $\mu_{i,t}(\theta_i)$ after observing the signal $\omega_{i,t+1}$ multiplied by the node's self reliance $a_{ii}$.
-The summation is the linear incorporation of the beilefs of $i$'s neighbors.
+Here the first term is the Bayesian update of the belief $\mu_{i,t}(\theta_k)$ after observing the signal $\omega_{i,t+1}$, multiplied by the node's self reliance $a_{ii}$.
+The summation is the linear incorporation of the beliefs of $i$'s neighbors.
 
@@
 
-Secondly, we must define $\mu_{j,t}(\theta_i)$ when $j$ is a DeGroot node.
+Secondly, we must define $\mu_{j,t}(\theta_k)$ when $j$ is a DeGroot node.
 We consider two methods for doing so, defined in sections \ref{sec:draw_from_degroot} and \ref{sec:likelihood_metric} respectively.
@@
 
-The first method that we consider for converting a DeGroot node $j$'s belief to a prior which can be included in a Non-Bayesian node $i$'s belief update involves generating a probability distribution from the $j$'s current belief and drawing from this distribution.
+We require a method for converting a DeGroot node $j$'s belief $m_{j,t} \in \mathbf{R}$ to a series of priors which can be included in a Non-Bayesian node $i$'s belief update.
+The first method we consider involves generating a probability distribution from the $j$'s current belief and drawing from this distribution.
 For each DeGroot neighbor of $i$ at time $t$ we define the probability distribution
@@
 p_{j,t}(x)=\begin{cases}
-m_{j,t} x + \frac{1}{2}(2-m^*) & 0 \le x \le 1 \\
+m_{j,t} x + \frac{1}{2}(2-m_{j,t}) & 0 \le x \le 1 \\
 0, & \text{otherwise}
@@
 \begin{equation}
-\mu_{j,t}^\prime(\theta_i) = \frac{\ell_i(s_{j,t}^\prime|\theta_i)}{m_{i,t}(s_{j,t}^\prime)}
+\mu_{j,t}^\prime(\theta_k) = \frac{\ell_i(s_{j,t}^\prime|\theta_k)}{\ell_i(s_{j,t}^\prime|\theta_0) + \ell_i(s_{j,t}^\prime|\theta_1) + ... + \ell_i(s_{j,t}^\prime|\theta_n)}
 \end{equation}
 
-This generated belief distribution $\mu_{j,t}^\prime$ is then used as
-
-% @todo[DDC] Still working on this section
+This generated belief distribution $\mu_{j,t}^\prime$ is then used for the values of $\mu_{j,t}(\theta_k)$ for the DeGroot node $j$ in the Non-Bayesian update of equation~\ref{eq:non_bayesian_update}.
 
@@
 \label{sec:likelihood_metric}
+
+The second method we consider for creating a probability distribution over the set of belief states $\Theta$ is to define an exponential distance metric such that
+
+\begin{equation}
+\mu_{j,t}^\prime(\theta_k) \propto e^{-(m_{j,t}-\hat{m_k})^2}
+\end{equation}
+where $\mu_{j,t}^\prime$ is the belief distribution which is used for the DeGroot node $j$'s values of $\mu_{j,t}(\theta_k)$ in the Non-Bayesian update of equation~\ref{eq:non_bayesian_update}.
+
+Since $\mu_{j,t}^\prime$ must be a probability distribution we must normalize the values for each state with the value
+
+\begin{equation}
+q_{j,t} = \sum_{k=1}^n e^{-(m_{j,t}-\hat{m_k})^2}
+\end{equation}
+
+Thus the calculation to create the DeGroot node's level of belief in each state $\theta_k$ is given by
+
+\begin{equation}
+\mu_{j,t}^\prime(\theta_k) = e^{-(m_{j,t}-\hat{m_i})^2} / q_{j,t}
+\end{equation}
 

### 2012-12-07 docs/paper.tex
Generalized model to allow for more probability distributions

@@
 \usepackage{amsmath} % For 'cases' curly brace
+\usepackage{amsfonts} % For bold number set font
 \begin{document}
@@
 
-We will represent the state of the world as a probability distribution:
+We will consider the state of the world to be a probability distribution $p^*(t) \in \mathbb{P}$.
+$\mathbb{P}$ is a pre-defined class of distributions where each  $p^*(t) \in \mathbb{P}$ is distinguishable by a single parameter.
+This single parameter $m^*$ where $\{m^* \in \mathbb{R}: m_{min} <= m^* <= m_{max} \}$  will be the state which the nodes in the network are attempting to learn.
+That is, $m^*$ is the ``true'' state of the world.
+\emph{A priori}, the nodes know the class of distribution but not the specific value of $m^*$; only that it lies uniformly in the range $[m_{min}, m_{max}]$.
+
+Our model allows for $\mathbb{P}$ to be any class of probability distribution as long as it can be completely specified by a single parameter $m^*$.
+Examples include the Poisson distribution with parameter $m^*$ and Gaussian distribution with mean $m^*$ and constant variance.
+We also introduce a trapezoidal probability distribution in section~\ref{sec:trapezoidal_distribution} which serves as a valid choice for $\mathbb{P}$.
+
+At each timestep $t$, every Non-Bayesian node $i$ will receive a signal $s_{i,t}$ which is a value drawn from $p^*(x)$.
+These observations will be used by the nodes in the network to construct a belief about $m^*$.
+
+\subsubsection{The Trapezoidal Distribution}
+\label{sec:trapezoidal_distribution}
+
+As an example of a class of distributions which can be used in our model we present the following trapezoidal distribution.
+
 \begin{equation}
@@
 
-The slope $\{ m^* \in \mathbf{R} : -2 \le m^* \le 2 \}$ will be the defining characteristic of the distribution.
+The slope $\{ m^* \in \mathbb{R} : m_{min} = -2 \le m^* \le 2 = m_{max} \}$ will be the defining characteristic of the distribution.
 We have chosen to bound $m^*$ between -2 and 2 and add the term $\frac{1}{2}(2-m^*)$ so that the support of $p^*(x)$  is always over $[0,1]$.
-The value of the parameter $m^*$ is the ``true'' state that each node is trying to learn.
-
-At each timestep $t$, every Non-Bayesian node $i$ will receive a signal $s_{i,t}$ which is a value drawn from $p^*(x)$.
-These observations will be used by the nodes in the network to construct a belief about $m^*$.
 
@@
 For a DeGroot node $i$, we represent the belief state of $i$ at time $t$ as a single value 
-$m_{i,t} \in \mathbf{R}$.
+$m_{i,t} \in \mathbb{R}$.
 However, belief of Non-Bayesian nodes is a probability distribution over a finite set of possible states of the world.
@@
 \label{eq:theta_meaning}
-\hat{m_k} = \frac{4k}{n - k} - 2
+\hat{m_k} = \frac{(m_{max} - m_{min})k}{n - 1} + m_{min}
 \end{equation}
-As an example, if we take n = 21 belief states, then we have
+As an example, if we take $n = 21$ belief states, $m_{min} = -2$, and $m_{max} = 2$, then we have
 \begin{equation}
@@
 % @todo[DDC] More detail for derivation/explanation of likelihood?
-In this case the likelihood function $\ell_i(s_i|\theta_k)$ can be obtained from the probability distribution function represented by the belief state $\theta_k$.
+The likelihood function $\ell_i(s_i|\theta_k)$ can be obtained from the probability distribution function represented by the belief state $\theta_k$.
+As an example, for the trapezoidal distribution described in section~\ref{sec:trapezoidal_distribution}, the likelihood function would be
 
@@
 \label{eq:likelihood}
-\ell_i(s_i|\theta_k) = \hat{m_k} s_i + \frac{1}{2}(2 - \hat{m_k})
+\ell_i(s_i|\theta_k) \propto \hat{m_k} s_i + \frac{1}{2}(2 - \hat{m_k})
 \end{equation}
@@
 
-We require a method for converting a DeGroot node $j$'s belief $m_{j,t} \in \mathbf{R}$ to a series of priors which can be included in a Non-Bayesian node $i$'s belief update.
-The first method we consider involves generating a probability distribution from the $j$'s current belief and drawing from this distribution.
-For each DeGroot neighbor of $i$ at time $t$ we define the probability distribution
+We require a method for converting a DeGroot node $j$'s belief $m_{j,t} \in \mathbb{R}$ to a series of priors which can be included in a Non-Bayesian node $i$'s belief update.
+The first method we consider involves generating a probability distribution $p_{j,t}$ from $j$'s belief at time $t$ and drawing from this distribution.
+The generated distribution is the $p_{j,t} \in \mathbb{P}$ where $j$'s belief $m_{j,t}$ is the single parameter defining the distribution.
+If $\mathbb{P}$ is the trapezoidal distribution defined in section~\ref{sec:trapezoidal_distribution}, then for each DeGroot neighbor of $i$ at time $t$ we have
+
 \begin{equation}
@@
 \begin{equation}
-\mu_{j,t}^\prime(\theta_k) = \frac{\ell_i(s_{j,t}^\prime|\theta_k)}{\ell_i(s_{j,t}^\prime|\theta_0) + \ell_i(s_{j,t}^\prime|\theta_1) + ... + \ell_i(s_{j,t}^\prime|\theta_n)}
+\mu_{j,t}^\prime(\theta_k) = \frac{\ell_i(s_{j,t}^\prime|\theta_k)}{\sum_{i=1}^{n} \ell_i(s_{j,t}^\prime|\theta_i)}
 \end{equation}

### 2012-12-07 src/eecs598/DeGrootNode.java
Convergence test for NonBayesian nodes, plus some experiments with a random graph (and a lot of smaller changes).

@@ -18,7 +18,7 @@ import eecs598.probability.ProbabilityUtil;
  * @author Pedro
  *
  */
-public class DeGrootNode implements Node {
+public class DeGrootNode extends Node {
 	
 	// TODO I am not considering the node's own estimate for the first time
 	// it receives a signal -- I am just copying the average of the neighbor's.
@@ -42,9 +42,9 @@ public class DeGrootNode implements Node {
 	 */
 	private List<Distribution> possibleDistributions;
 	
-	public DeGrootNode(ParameterEstimator parameterEstimator,
+	public DeGrootNode(int id, ParameterEstimator parameterEstimator,
 			BeliefEstimator beliefEstimator) {
-		super();
+		super(id);
 		this.parameterEstimator = parameterEstimator;
 		this.beliefEstimator = beliefEstimator;
 	}

### 2012-12-07 src/eecs598/Node.java

@@ -6,24 +6,57 @@ import java.util.List;
 
 import eecs598.probability.Distribution;
 
-public interface Node {
+public abstract class Node {
+	
+	private int id;
+	
+	public Node(int id) {
+		super();
+		this.id = id;
+	}
+
+	public int getId() {
+		return this.id;
+	}
 	
 	/**
 	 * Updates the node's beliefs according to the new signal
 	 * We pass the graph in case nodes want to use information from neighbors.
 	 * @param signal
 	 */
-	public void newSignal(Collection<Node> neighbors, double signal);
+	public abstract void newSignal(Collection<Node> neighbors, double signal);
 	
 	/**
 	 * Returns the node's current set of beliefs on possible states.
 	 * @return
 	 */
-	public HashMap<Double, Double> getBeliefs();
+	public abstract HashMap<Double, Double> getBeliefs();
 	
 	/**
 	 * Sets the list of possible distributions.
 	 * @param distributions
 	 */
-	public void setPossibleDistributions(List<Distribution> distributions);
+	public abstract void setPossibleDistributions(List<Distribution> distributions);
+
+	@Override
+	public int hashCode() {
+		final int prime = 31;
+		int result = 1;
+		result = prime * result + id;
+		return result;
+	}
+
+	@Override
+	public boolean equals(Object obj) {
+		if (this == obj)
+			return true;
+		if (obj == null)
+			return false;
+		if (getClass() != obj.getClass())
+			return false;
+		Node other = (Node) obj;
+		if (id != other.id)
+			return false;
+		return true;
+	}
 }

### 2012-12-07 src/eecs598/NonBayesianNode.java

@@ -9,7 +9,7 @@ import java.util.Map;
 import eecs598.probability.Distribution;
 import eecs598.probability.ProbabilityUtil;
 
-public class NonBayesianNode implements Node {
+public class NonBayesianNode extends Node {
 
 	/**
 	 * Associates each possible distribution to a belief between
@@ -21,11 +21,9 @@ public class NonBayesianNode implements Node {
 	 * An order list of possible distributions.
 	 */
 	private List<Distribution> distributions;
-	
-	private int id;
-	
+		
 	public NonBayesianNode(int id, List<Distribution> possibleDistributions) {
-		this.id = id;
+		super(id);
 		setPossibleDistributions(possibleDistributions);
 	}
 	
@@ -149,34 +147,8 @@ public class NonBayesianNode implements Node {
 		return new HashMap<>(beliefs);
 	}
 
-	public int getId() {
-		return id;
-	}
-
 	@Override
 	public String toString() {
-		return "NonBayesianNode " + id + " [" + beliefs + "]";
+		return "NonBayesianNode " + getId() + " [" + beliefs + "]";
 	}
-
-	@Override
-	public int hashCode() {
-		final int prime = 31;
-		int result = 1;
-		result = prime * result + id;
-		return result;
-	}
-
-	@Override
-	public boolean equals(Object obj) {
-		if (this == obj)
-			return true;
-		if (obj == null)
-			return false;
-		if (getClass() != obj.getClass())
-			return false;
-		NonBayesianNode other = (NonBayesianNode) obj;
-		if (id != other.id)
-			return false;
-		return true;
-	}	
 }

### 2012-12-07 src/eecs598/RandomDrawBeliefEstimator.java

@@ -3,8 +3,8 @@ package eecs598;
 import java.util.HashMap;
 import java.util.List;
 
+import eecs598.factories.probability.DistributionFactory;
 import eecs598.probability.Distribution;
-import eecs598.probability.DistributionFactory;
 import eecs598.probability.ProbabilityUtil;
 
 /**

### 2012-12-07 src/eecs598/experiments/ConvergenceInspector.java

@@ -1,0 +1,110 @@
+package eecs598.experiments;
+
+import java.util.ArrayList;
+import java.util.Collection;
+import java.util.Map;
+
+import eecs598.DeGrootNode;
+import eecs598.Node;
+import eecs598.NonBayesianNode;
+import eecs598.util.DoubleEquals;
+
+/**
+ * Examines a collection and node and returns information about the
+ * convergence.
+ * @author Pedro
+ *
+ */
+public class ConvergenceInspector {
+	
+	private final double beliefConvergenceThreshold = 0.00001;
+	
+	/**
+	 * We define convergence as:
+	 * 	- For NonBayesian: all nodes agreeing that a particular parameter has likelihood 1.
+	 *  - For DeGroot: all nodes agreeing on the same parameter estimate.
+	 *  - Total convergence: the DeGroot nodes' estimate matches the NonBayesian belief.
+	 * @param nodes all nodes in the graph.
+	 * @return
+	 */
+	public boolean haveConverged(Collection<Node> nodes) {
+		// TODO look at DeGroot nodes too!
+		Collection<NonBayesianNode> nonBayesianNodes = new ArrayList<>();
+		Collection<DeGrootNode> deGrootNodes = new ArrayList<>();
+		
+		separateNodeTypes(nodes, nonBayesianNodes, deGrootNodes, null);
+		
+		return haveNonBayesianNodesConverged(nonBayesianNodes);
+	}
+	
+	public double getConvergedParameter(Collection<Node> nodes) {
+		// TODO look at DeGroot nodes too!
+		Collection<NonBayesianNode> nonBayesianNodes = new ArrayList<>();
+		Collection<DeGrootNode> deGrootNodes = new ArrayList<>();
+		
+		separateNodeTypes(nodes, nonBayesianNodes, deGrootNodes, null);
+		
+		return getNonBayesianConvergedParameter(nonBayesianNodes);
+	}
+	
+	protected void separateNodeTypes(Collection<Node> allNodes,
+			Collection<NonBayesianNode> nonBayesianNodes,
+			Collection<DeGrootNode> deGrootNodes,
+			Collection<Node> otherNodes) {
+		for(Node node : allNodes) {
+			if(node instanceof NonBayesianNode) {
+				nonBayesianNodes.add((NonBayesianNode)node);
+			} else if(node instanceof DeGrootNode) {
+				deGrootNodes.add((DeGrootNode)node);
+			} else if(otherNodes != null) {
+				otherNodes.add(node);
+			}
+		}
+	}
+	
[…]

### 2012-12-07 src/eecs598/experiments/DistributionRepository.java

@@ -1,0 +1,69 @@
+package eecs598.experiments;
+
+import java.util.ArrayList;
+import java.util.List;
+import java.util.Random;
+
+import eecs598.probability.Distribution;
+import eecs598.probability.Gaussian;
+import eecs598.test.helpers.TestDistributions;
+
+public class DistributionRepository {
+	/**
+	 * Returns one "distribution" whose pdf is 0 everywhere and a uniform distribution
+	 * whose "parameter" is the method's argument. Used as a sanity check -- all NB nodes
+	 * should converge to the uniform distribution in one timestep. 
+	 * @return the true distribution (i.e. the uniform)
+	 */
+	public static Distribution getZeroAndUniform(int uniformDistroId, List<Distribution> possibleDistributions) {
+		if(uniformDistroId == 0) {
+			throw new IllegalArgumentException("The ID for the uniform distribution cannot be 0.");
+		}
+		Distribution zero = new TestDistributions.ZeroPdf(0);
+		Distribution uniform = new TestDistributions.Uniform(uniformDistroId);
+		
+		possibleDistributions.add(zero);
+		possibleDistributions.add(uniform);
+		
+		return uniform;
+	}
+	
+	/**
+	 * Creates two Gaussians really far apart.
+	 * @param possibleDistributions
+	 * @return
+	 */
+	public static Distribution getTwoGaussiansEasy(List<Distribution> possibleDistributions) {
+		throwIfNotEmpty(possibleDistributions);
+
+		possibleDistributions.add(new Gaussian(2.0));
+		possibleDistributions.add(new Gaussian(20.0));	
+		
+		return chooseRandom(possibleDistributions);
+	}
+	
+	/**
+	 * Creates two Gaussians close to each other.
+	 * @param possibleDistributions
+	 * @return
+	 */
+	public static Distribution getTwoGaussiansHard(List<Distribution> possibleDistributions) {
+		throwIfNotEmpty(possibleDistributions);
+
+		possibleDistributions.add(new Gaussian(10.0));
+		possibleDistributions.add(new Gaussian(9.0));	
+		
+		return chooseRandom(possibleDistributions);
+	}
+	
+	private static void throwIfNotEmpty(List<Distribution> list) {
+		if(!list.isEmpty()) {
+			throw new IllegalArgumentException("List of possible distributions must be empty.");
+		}
+	}
+	
+	private static Distribution chooseRandom(List<Distribution> list) {
+		Random rnd = new Random();
+		return list.get(rnd.nextInt(list.size()));
+	}
+}

### 2012-12-07 src/eecs598/experiments/ExperimentController.java

@@ -1,0 +1,32 @@
+package eecs598.experiments;
+
+import java.util.Collection;
+
+import edu.uci.ics.jung.graph.Graph;
+import eecs598.Edge;
+import eecs598.Node;
+import eecs598.probability.Distribution;
+
+/**
+ * Runs an experiment, drawing values from the true distribution and feeding them
+ * to every node in the graph.
+ * @author Pedro
+ *
+ */
+public class ExperimentController {
+	private Distribution trueDistribution;
+
+	public ExperimentController(Distribution trueDistribution) {
+		super();
+		this.trueDistribution = trueDistribution;
+	}
+	
+	public void run(Graph<Node, Edge> graph, int numTimesteps) {
+		for(int i = 0; i < numTimesteps; i++) {
+			Collection<Node> nodes = graph.getVertices();
+			for(Node node : nodes) {
+				node.newSignal(graph.getNeighbors(node), trueDistribution.draw());
+			}
+		}
+	}
+}

### 2012-12-07 src/eecs598/experiments/OnlyNonBayesian.java

@@ -1,0 +1,84 @@
+package eecs598.experiments;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import org.apache.commons.collections15.Factory;
+
+import edu.uci.ics.jung.algorithms.generators.random.ErdosRenyiGenerator;
+import edu.uci.ics.jung.graph.Graph;
+import edu.uci.ics.jung.graph.UndirectedGraph;
+import eecs598.Edge;
+import eecs598.Node;
+import eecs598.factories.EdgeFactory;
+import eecs598.factories.GraphFactory;
+import eecs598.factories.RatioNodeFactory;
+import eecs598.probability.Distribution;
+
+public class OnlyNonBayesian {
+	
+	private List<Distribution> possibleDistributions;
+	private Factory<Node> nodeFactory; 
+	private Factory<Edge> edgeFactory;
+	private Factory<UndirectedGraph<Node, Edge>> graphFactory;
+		
+	public OnlyNonBayesian(List<Distribution> possibleDistributions) {
+		super();
+		this.possibleDistributions = possibleDistributions;
+		this.nodeFactory = new RatioNodeFactory(1.0, possibleDistributions, null, null);
+		this.edgeFactory = new EdgeFactory();
+		this.graphFactory = new GraphFactory();
+	}
+
+	public void runErdosRenyi(ExperimentController controller, int numVertices, double p) {
+		ErdosRenyiGenerator<Node, Edge> erdosRenyiGenerator = new ErdosRenyiGenerator<Node, Edge>(
+				graphFactory, nodeFactory, edgeFactory, numVertices, p);
+		
+		Graph<Node, Edge> graph = erdosRenyiGenerator.create();
+		
+		controller.run(graph, 1000);
+		
+		ConvergenceInspector convergenceInspector = new ConvergenceInspector();
+		boolean converged = convergenceInspector.haveConverged(graph.getVertices());
+		System.out.println("\tConvergence: " + converged);
+		if(converged) {
+			System.out.println("\tParameter: " + convergenceInspector.getConvergedParameter(graph.getVertices()));
+		}
+	}
+	
+	public static void runSanityCheck() {
+		int uniformId = 42;
+		System.out.println("SanityCheck: Zero and Uniform, Uniform ID = " + uniformId);
+		List<Distribution> possibleDistributions = new ArrayList<>();
[…]

### 2012-12-07 src/eecs598/factories/GraphFactory.java

@@ -1,0 +1,17 @@
+package eecs598.factories;
+
+import org.apache.commons.collections15.Factory;
+
+import edu.uci.ics.jung.graph.SparseGraph;
+import edu.uci.ics.jung.graph.UndirectedGraph;
+import edu.uci.ics.jung.graph.UndirectedSparseGraph;
+import eecs598.Edge;
+import eecs598.Node;
+
+public class GraphFactory implements Factory<UndirectedGraph<Node, Edge>> {
+
+	@Override
+	public UndirectedGraph<Node, Edge> create() {
+		return new UndirectedSparseGraph<Node, Edge>();
+	}
+}

### 2012-12-07 src/eecs598/factories/RatioNodeFactory.java

@@ -1,0 +1,57 @@
+package eecs598.factories;
+
+import java.util.List;
+import java.util.Random;
+
+import org.apache.commons.collections15.Factory;
+
+import eecs598.BeliefEstimator;
+import eecs598.DeGrootNode;
+import eecs598.Node;
+import eecs598.NonBayesianNode;
+import eecs598.ParameterEstimator;
+import eecs598.probability.Distribution;
+
+/**
+ * This factory creates nodes in a given ratio of NonBayesian to DeGroot, e.g.
+ * 79% NonBayesian.
+ * @author Pedro
+ *
+ */
+public class RatioNodeFactory implements Factory<Node> {
+
+	private double nonBayesianRatio;
+	private Random random = new Random();
+	
+	int nodeCounter = 1; // used for node ids
+	
+	List<Distribution> possibleDistributions; // NonBayesian nodes need this.
+	ParameterEstimator parameterEstimator; // DeGroot nodes need this.
+	BeliefEstimator beliefEstimator; // DeGroot nodes need this.
+
+	public RatioNodeFactory(double nonBayesianRatio,
+			List<Distribution> possibleDistributions,
+			ParameterEstimator parameterEstimator,
+			BeliefEstimator beliefEstimator) {
+		super();
+		this.nonBayesianRatio = nonBayesianRatio;
+		this.possibleDistributions = possibleDistributions;
+		this.parameterEstimator = parameterEstimator;
+		this.beliefEstimator = beliefEstimator;
+	}
+
+	@Override
+	/**
+	 * Creates either a non-bayesian or a DeGroot node.
+	 */
+	public Node create() {
+		Node node = null;
+		if(random.nextDouble() <= nonBayesianRatio) {
+			node = new NonBayesianNode(nodeCounter, possibleDistributions);
+		} else {
+			node = new DeGrootNode(nodeCounter, parameterEstimator, beliefEstimator);
+		}
+		nodeCounter++;
+		return node;
+	}
+}

### 2012-12-07 src/eecs598/factories/probability/DistributionFactory.java

@@ -1,4 +1,6 @@
-package eecs598.probability;
+package eecs598.factories.probability;
+
+import eecs598.probability.Distribution;
 
 public interface DistributionFactory {
 	public Distribution create(double parameter);

### 2012-12-07 src/eecs598/factories/probability/GaussianFactory.java

@@ -1,0 +1,13 @@
+package eecs598.factories.probability;
+
+import eecs598.probability.Distribution;
+import eecs598.probability.Gaussian;
+
+public class GaussianFactory implements DistributionFactory {
+
+	@Override
+	public Distribution create(double mean) {
+		return new Gaussian(mean);
+	}
+
+}

### 2012-12-07 src/eecs598/factories/probability/TrapezoidFactory.java

@@ -1,4 +1,7 @@
-package eecs598.probability;
+package eecs598.factories.probability;
+
+import eecs598.probability.Distribution;
+import eecs598.probability.TrapezoidDistribution;
 
 public class TrapezoidFactory implements DistributionFactory {
 

### 2012-12-07 src/eecs598/probability/Gaussian.java

@@ -1,0 +1,33 @@
+package eecs598.probability;
+
+import cern.jet.random.Normal;
+import cern.jet.random.engine.RandomEngine;
+
+public class Gaussian implements Distribution {
+
+	private Normal normal;
+	private double mean;
+	
+	private final double stdDev = 1;
+	
+	public Gaussian(double mean) {
+		this.mean = mean;
+		this.normal = new Normal(mean, stdDev, RandomEngine.makeDefault());
+	}
+	
+	@Override
+	public double draw() {
+		return normal.nextDouble();
+	}
+
+	@Override
+	public double pdf(double x) {
+		return normal.pdf(x);
+	}
+
+	@Override
+	public double getParameter() {
+		return mean;
+	}
+
+}

### 2012-12-07 src/eecs598/test/ConvergenceInsepctorTest.java

@@ -1,0 +1,87 @@
+package eecs598.test;
+
+import static org.junit.Assert.*;
+
+import java.util.ArrayList;
+import java.util.Collection;
+import java.util.List;
+
+import org.junit.Test;
+
+import eecs598.Node;
+import eecs598.NonBayesianNode;
+import eecs598.experiments.ConvergenceInspector;
+import eecs598.probability.Distribution;
+import eecs598.test.helpers.TestDistributions;
+
+/**
+ * Some of the tests here are copied from other test cases.
+ * @author Pedro
+ *
+ */
+public class ConvergenceInsepctorTest {
+
+	@Test
+	public void testSingleNodeConvergence() {
+		//
+		// Simplest test possible: one node with a signal s.t. it can tell the right
+		// distribution with 100% likelihood. We use a distribution called ZeroPdf whose
+		// pdf always returns 0 to simulate this.
+		//
+		Distribution uniform = new TestDistributions.Uniform(1);
+		Distribution zero = new TestDistributions.ZeroPdf(0);
+		
+		List<Distribution> distributions = new ArrayList<Distribution>();
+		distributions.add(uniform); distributions.add(zero);
+		
+		NonBayesianNode node = new NonBayesianNode(1, distributions);
+		
+		node.newSignal(new ArrayList<Node>(), 0.2);
+		
+		ConvergenceInspector inspector = new ConvergenceInspector();
+		Collection<Node> nodes = new ArrayList<Node>();
+		nodes.add(node);
+		assertTrue(inspector.haveConverged(nodes));
+		assertEquals(1.0, inspector.getConvergedParameter(nodes), 0.0000001);
+	}
+
+	@Test
+	public void testOneHundredNodes() {
+		//
+		// Like testTwoNodes but with a lot more nodes so that A should converge.
+		//
+
+		Distribution zero = new TestDistributions.ZeroPdf(2); // zero and uniform2 have the same id
+		Distribution uniform1 = new TestDistributions.Uniform(1);
+		Distribution uniform2 = new TestDistributions.Uniform(2);
+		
+		List<Distribution> distributionsA = new ArrayList<Distribution>();
+		distributionsA.add(uniform1); distributionsA.add(uniform2);
+		
+		List<Distribution> distributionsB = new ArrayList<Distribution>();
[…]

### 2012-12-07 src/eecs598/test/DeGrootNodeTest.java

@@ -18,8 +18,8 @@ public class DeGrootNodeTest {
 
 	@Test
 	public void testOneNeighbor() {
-		ExpectedValueNode neighbor = new ExpectedValueNode(42.0);
-		DeGrootNode node = new DeGrootNode(new NopParameterEstimator(),
+		ExpectedValueNode neighbor = new ExpectedValueNode(1, 42.0);
+		DeGrootNode node = new DeGrootNode(2, new NopParameterEstimator(),
 				new RandomDrawBeliefEstimator(new TestDistributions.UniformFactory()));
 		
 		List<Node> nodeNeighbors = new ArrayList<Node>();
@@ -32,9 +32,9 @@ public class DeGrootNodeTest {
 	
 	@Test
 	public void testTwoNeighbors() {
-		ExpectedValueNode neighbor1 = new ExpectedValueNode(42.0);
-		ExpectedValueNode neighbor2 = new ExpectedValueNode(0);
-		DeGrootNode node = new DeGrootNode(new NopParameterEstimator(),
+		ExpectedValueNode neighbor1 = new ExpectedValueNode(1, 42.0);
+		ExpectedValueNode neighbor2 = new ExpectedValueNode(2, 0);
+		DeGrootNode node = new DeGrootNode(3, new NopParameterEstimator(),
 				new RandomDrawBeliefEstimator(new TestDistributions.UniformFactory()));
 		
 		List<Node> nodeNeighbors = new ArrayList<Node>();

### 2012-12-07 src/eecs598/test/RandomDrawBeliefEstimatorTest.java

@@ -9,8 +9,8 @@ import java.util.List;
 import org.junit.Test;
 
 import eecs598.RandomDrawBeliefEstimator;
+import eecs598.factories.probability.DistributionFactory;
 import eecs598.probability.Distribution;
-import eecs598.probability.DistributionFactory;
 import eecs598.test.helpers.TestDistributions;
 
 public class RandomDrawBeliefEstimatorTest {

### 2012-12-07 src/eecs598/test/helpers/ExpectedValueNode.java

@@ -13,9 +13,10 @@ import eecs598.probability.Distribution;
  * @author Pedro
  *
  */
-public class ExpectedValueNode implements Node {
+public class ExpectedValueNode extends Node {
 	private double expectedValue = 0;
-	public ExpectedValueNode(double expectedBeliefValue) {
+	public ExpectedValueNode(int id, double expectedBeliefValue) {
+		super(id);
 		this.expectedValue = expectedBeliefValue;
 	}
 	

### 2012-12-07 src/eecs598/test/helpers/TestDistributions.java

@@ -2,8 +2,8 @@ package eecs598.test.helpers;
 
 import java.util.Random;
 
+import eecs598.factories.probability.DistributionFactory;
 import eecs598.probability.Distribution;
-import eecs598.probability.DistributionFactory;
 import eecs598.util.NotImplementedException;
 
 public class TestDistributions {

### 2012-12-08 src/eecs598/DeGrootNode.java
Main changes: running convergence tests for mixed graphs (NB and DG); new BeliefEstimator that samples and computes the PDF several times (the simple one doesn't work in practice); rough graph visualization. Experimentation code is a little messy.

@@ -6,6 +6,7 @@ import java.util.List;
 
 import eecs598.probability.Distribution;
 import eecs598.probability.ProbabilityUtil;
+import eecs598.util.Util;
 
 /**
  * Represents a DeGroot node, which maintains an estimate of the parameter. The main
@@ -49,6 +50,15 @@ public class DeGrootNode extends Node {
 		this.beliefEstimator = beliefEstimator;
 	}
 
+	public DeGrootNode(int id, ParameterEstimator parameterEstimator,
+			BeliefEstimator beliefEstimator,
+			List<Distribution> possibleDistributions) {
+		super(id);
+		this.parameterEstimator = parameterEstimator;
+		this.beliefEstimator = beliefEstimator;
+		this.possibleDistributions = possibleDistributions;
+	}
+
 	@Override
 	public void newSignal(Collection<Node> neighbors, double signal) {
 		//
@@ -68,20 +78,32 @@ public class DeGrootNode extends Node {
 		//
 		
 		if(!firstSignal) {
-			sumEstimates += this.estimate;
-			sumWeights += getNeighborInfluence(this, neighbors); // self-influence
+//			double weight = getNeighborInfluence(this, neighbors); // self-influence
+//			sumEstimates += weight*this.estimate;
+//			sumWeights +=  weight; 
 		} else {
 			firstSignal = false;
 		}
 		
 		for(Node neighbor : neighbors) {
+			//if(neighbor instanceof NonBayesianNode) {
+			// XXX test code!
 			double weight = getNeighborInfluence(neighbor, neighbors);
 			double weightedEstimate = weight * ProbabilityUtil.expectedValue(neighbor.getBeliefs());
 			sumEstimates += weightedEstimate;
 			sumWeights += weight;
+			
+				
+			//}
 		}
 		
-		this.estimate = sumEstimates / sumWeights;
+		if(sumWeights > 0) {
+			this.estimate = sumEstimates / sumWeights;
+		} else {
+			this.estimate = 0;
+		}
+		
+		Util.throwIfNaN(this.estimate);
 	}
 	
 	/**
@@ -93,7 +115,7 @@ public class DeGrootNode extends Node {
 	 */
 	protected double getNeighborInfluence(Node neighbor, Collection<Node> neighbors) {
 		// TODO This is copy/paste from NonBayesianNode.. Code smell
-		
+
 		//
 		// We just have a uniform distribution.
 		//
[…]

### 2012-12-08 src/eecs598/NonBayesianNode.java

@@ -8,6 +8,7 @@ import java.util.Map;
 
 import eecs598.probability.Distribution;
 import eecs598.probability.ProbabilityUtil;
+import eecs598.util.Util;
 
 public class NonBayesianNode extends Node {
 
@@ -92,6 +93,7 @@ public class NonBayesianNode extends Node {
 				double parameter = paramBeliefPair.getKey();
 				double belief = paramBeliefPair.getValue();
 				double weightedNeighborBelief = influence * belief;
+				Util.throwIfNaN(weightedNeighborBelief);
 				//
 				// Update our belief by adding the weighted neighbor's.
 				//

### 2012-12-08 src/eecs598/RandomDrawBeliefEstimator.java

@@ -22,7 +22,7 @@ public class RandomDrawBeliefEstimator implements BeliefEstimator {
 	 * This class creates parametrized distributions. We use it to construct
 	 * a customized distribution with our current estimate of the parameter.
 	 */
-	private DistributionFactory distributionFactory;
+	protected DistributionFactory distributionFactory;
 	
 	public RandomDrawBeliefEstimator(DistributionFactory distributionFactory) {
 		super();
@@ -47,6 +47,9 @@ public class RandomDrawBeliefEstimator implements BeliefEstimator {
 		double randomSample = estimatedDistribution.draw();
 		for(Distribution candidate : possibleDistributions) {
 			double pdf = candidate.pdf(randomSample);
+			if(Double.isNaN(pdf) || Double.isInfinite(pdf)) {
+				throw new IllegalStateException("Invalid probability");
+			}
 			beliefs.put(candidate.getParameter(), pdf);
 		}
 		

### 2012-12-08 src/eecs598/experiments/DistributionRepository.java

@@ -62,6 +62,28 @@ public class DistributionRepository {
 		}
 	}
 	
+	public static Distribution getNGaussiansEasy(int n, List<Distribution> possibleDistributions) {
+		throwIfNotEmpty(possibleDistributions);
+		double startingMean = 5.0;
+		double step = 10;
+		for(int i = 0; i < n; i++) {
+			possibleDistributions.add(new Gaussian(startingMean += i*step));
+		}
+		
+		return chooseRandom(possibleDistributions);
+	}
+	
+	public static Distribution getNGaussiansHard(int n, List<Distribution> possibleDistributions) {
+		throwIfNotEmpty(possibleDistributions);
+		double startingMean = 5.0;
+		double step = 1;
+		for(int i = 0; i < n; i++) {
+			possibleDistributions.add(new Gaussian(startingMean += i*step));
+		}
+		
+		return chooseRandom(possibleDistributions);
+	}
+	
 	private static Distribution chooseRandom(List<Distribution> list) {
 		Random rnd = new Random();
 		return list.get(rnd.nextInt(list.size()));

### 2012-12-08 src/eecs598/experiments/ExperimentController.java

@@ -1,10 +1,13 @@
 package eecs598.experiments;
 
+import java.util.ArrayList;
 import java.util.Collection;
+import java.util.List;
 
 import edu.uci.ics.jung.graph.Graph;
 import eecs598.Edge;
 import eecs598.Node;
+import eecs598.experiments.analyzer.ExperimentAnalyzer;
 import eecs598.probability.Distribution;
 
 /**
@@ -15,18 +18,31 @@ import eecs598.probability.Distribution;
  */
 public class ExperimentController {
 	private Distribution trueDistribution;
-
+	List<ExperimentAnalyzer> analyzers = new ArrayList<>();
+	
 	public ExperimentController(Distribution trueDistribution) {
 		super();
 		this.trueDistribution = trueDistribution;
 	}
 	
+	public void attachAnalyzer(ExperimentAnalyzer analyzer) {
+		this.analyzers.add(analyzer);
+	}
+	
 	public void run(Graph<Node, Edge> graph, int numTimesteps) {
+		notifyAllAnalyzers(0, graph);
 		for(int i = 0; i < numTimesteps; i++) {
 			Collection<Node> nodes = graph.getVertices();
 			for(Node node : nodes) {
 				node.newSignal(graph.getNeighbors(node), trueDistribution.draw());
 			}
+			notifyAllAnalyzers(i+1, graph);
+		}
+	}
+	
+	public void notifyAllAnalyzers(int timestep, Graph<Node, Edge> graph) {
+		for(ExperimentAnalyzer analyzer : analyzers) {
+			analyzer.notifyTimestep(graph, timestep);
 		}
 	}
 }

### 2012-12-08 src/eecs598/experiments/OnlyNonBayesian.java

@@ -3,48 +3,23 @@ package eecs598.experiments;
 import java.util.ArrayList;
 import java.util.List;
 
-import org.apache.commons.collections15.Factory;
-
-import edu.uci.ics.jung.algorithms.generators.random.ErdosRenyiGenerator;
-import edu.uci.ics.jung.graph.Graph;
-import edu.uci.ics.jung.graph.UndirectedGraph;
-import eecs598.Edge;
-import eecs598.Node;
-import eecs598.factories.EdgeFactory;
-import eecs598.factories.GraphFactory;
-import eecs598.factories.RatioNodeFactory;
+import eecs598.experiments.analyzer.AverageBeliefTracker;
 import eecs598.probability.Distribution;
 
-public class OnlyNonBayesian {
+public class OnlyNonBayesian extends RatioNonBayesianDeGroot {
 	
-	private List<Distribution> possibleDistributions;
-	private Factory<Node> nodeFactory; 
-	private Factory<Edge> edgeFactory;
-	private Factory<UndirectedGraph<Node, Edge>> graphFactory;
-		
+	
+	
 	public OnlyNonBayesian(List<Distribution> possibleDistributions) {
-		super();
-		this.possibleDistributions = possibleDistributions;
-		this.nodeFactory = new RatioNodeFactory(1.0, possibleDistributions, null, null);
-		this.edgeFactory = new EdgeFactory();
-		this.graphFactory = new GraphFactory();
+		super(1.0, possibleDistributions, null);
 	}
 
-	public void runErdosRenyi(ExperimentController controller, int numVertices, double p) {
-		ErdosRenyiGenerator<Node, Edge> erdosRenyiGenerator = new ErdosRenyiGenerator<Node, Edge>(
-				graphFactory, nodeFactory, edgeFactory, numVertices, p);
-		
-		Graph<Node, Edge> graph = erdosRenyiGenerator.create();
-		
-		controller.run(graph, 1000);
-		
-		ConvergenceInspector convergenceInspector = new ConvergenceInspector();
-		boolean converged = convergenceInspector.haveConverged(graph.getVertices());
-		System.out.println("\tConvergence: " + converged);
-		if(converged) {
-			System.out.println("\tParameter: " + convergenceInspector.getConvergedParameter(graph.getVertices()));
-		}
+	public static void main(String[] args) {
+		//runSanityCheck();
+		//run2GaussiansEasy();
[…]

### 2012-12-08 src/eecs598/experiments/analyzer/AverageBeliefTracker.java

@@ -1,0 +1,84 @@
+package eecs598.experiments.analyzer;
+
+import java.io.BufferedWriter;
+import java.io.PrintStream;
+import java.util.ArrayList;
+import java.util.Collection;
+import java.util.Collections;
+import java.util.Iterator;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+
+import edu.uci.ics.jung.graph.Graph;
+import eecs598.Edge;
+import eecs598.Node;
+import eecs598.NonBayesianNode;
+
+/**
+ * This analyzer plots the average belief in all possible parameter values.
+ * It outputs data in the following format:
+ * TIMESTEP HYPOTHESIS1 HYPOTHESIS1_BELIEF HYPOTHESIS2 HYPOTHESIS2_BELIEF .... HYPOTHESISN HYPOTHESISN_BELIEF
+ * 
+ * where each column is separated by tabs, every hypothesis is a possible parameter,  and
+ * hypothesisi_belief is the average belief in [0, 1] over all nodes in that hypothesis.
+ * 
+ * @author Pedro
+ *
+ */
+public class AverageBeliefTracker implements ExperimentAnalyzer {
+	
+	/**
+	 * Where to output data.
+	 */
+	private PrintStream stream;	
+	
+	private NodeType nodeTypeToBeTracked;
+
+
+	public AverageBeliefTracker(PrintStream stream) {
+		super();
+		this.stream = stream;
+		this.nodeTypeToBeTracked = NodeType.All;
+	}
+		
+	public AverageBeliefTracker(PrintStream stream, NodeType nodeTypeToBeTracked) {
+		super();
+		this.stream = stream;
+		this.nodeTypeToBeTracked = nodeTypeToBeTracked;
+	}
+
+
+	public PrintStream getStream() {
+		return stream;
+	}
+
+
+	public void setStream(PrintStream stream) {
+		this.stream = stream;
+	}
+
+
+	public NodeType getNodeTypeToBeTracked() {
+		return nodeTypeToBeTracked;
+	}
+
+
+	public void setNodeTypeToBeTracked(NodeType nodeTypeToBeTracked) {
+		this.nodeTypeToBeTracked = nodeTypeToBeTracked;
+	}
+
+
+	@Override
+	public void notifyTimestep(Graph<Node, Edge> graph, int timestep) {
+		Collection<Node> nodes = graph.getVertices();
[…]

### 2012-12-08 src/eecs598/experiments/analyzer/AverageParameterEstimateTracker.java

@@ -1,0 +1,49 @@
+package eecs598.experiments.analyzer;
+
+import java.io.PrintStream;
+import java.util.Collection;
+import java.util.List;
+
+import edu.uci.ics.jung.graph.Graph;
+import eecs598.Edge;
+import eecs598.Node;
+
+/**
+ * Tracks the parameter estimate average for DeGroot nodes.
+ * @author Pedro
+ *
+ */
+public class AverageParameterEstimateTracker implements ExperimentAnalyzer {
+	
+	/**
+	 * Where to output data.
+	 */
+	private PrintStream stream;	
+	
+	private NodeType nodeTypeToBeTracked;
+
+
+	public AverageParameterEstimateTracker(PrintStream stream) {
+		super();
+		this.stream = stream;
+	}
+	
+	public PrintStream getStream() {
+		return stream;
+	}
+
+
+	public void setStream(PrintStream stream) {
+		this.stream = stream;
+	}
+
+	@Override
+	public void notifyTimestep(Graph<Node, Edge> graph, int timestep) {
+		Collection<Node> nodes = graph.getVertices();
+		Double averageParamEstimate = AverageParameterEstimate.getAverageParameterEstimate(nodes);
+		StringBuilder logBlder = new StringBuilder();
+		logBlder.append(timestep).append("\t").append(averageParamEstimate);
+		stream.println(logBlder.toString());
+	}
+
+}

### 2012-12-08 src/eecs598/experiments/analyzer/NodeType.java

@@ -1,0 +1,7 @@
+package eecs598.experiments.analyzer;
+
+public enum NodeType {
+	NonBayesian,
+	DeGroot,
+	All
+}

### 2012-12-08 src/eecs598/experiments/visualization/Transformers.java

@@ -1,0 +1,54 @@
+package eecs598.experiments.visualization;
+
+import java.awt.Color;
+import java.awt.Paint;
+import java.awt.Rectangle;
+import java.awt.Shape;
+import java.awt.geom.Ellipse2D;
+
+import org.apache.commons.collections15.Transformer;
+
+import eecs598.DeGrootNode;
+import eecs598.Node;
+import eecs598.NonBayesianNode;
+import eecs598.probability.ProbabilityUtil;
+
+public class Transformers {
+	public static class VertexFillPaint implements Transformer<Node, Paint> {
+
+		@Override
+		public Paint transform(Node node) {
+			if(node instanceof NonBayesianNode) {
+				return Color.GREEN;
+			} else {
+				return Color.GRAY;
+			}
+		}
+		
+	}
+	
+	public static class VertexShape implements Transformer<Node, Shape> {
+
+		@Override
+		public Shape transform(Node node) {
+			if(node instanceof NonBayesianNode) {
+				return new Ellipse2D.Double(-10, -10, 20, 20);
+			} else {
+				return new Rectangle(-10, -10, 20, 20);
+			}
+		}
+		
+	}
+	
+	public static class VertexLabel implements Transformer<Node, String> {
+
+		@Override
+		public String transform(Node node) {
+			if(node instanceof NonBayesianNode) {
+				return String.format("%.2f", ProbabilityUtil.expectedValue(node.getBeliefs()));
+			} else {
+				return String.format("%.2f", ((DeGrootNode)node).getParameterEstimate());
+			}
+		}
+	}
+}

### 2012-12-08 src/eecs598/factories/RatioNodeFactory.java

@@ -49,7 +49,7 @@ public class RatioNodeFactory implements Factory<Node> {
 		if(random.nextDouble() <= nonBayesianRatio) {
 			node = new NonBayesianNode(nodeCounter, possibleDistributions);
 		} else {
-			node = new DeGrootNode(nodeCounter, parameterEstimator, beliefEstimator);
+			node = new DeGrootNode(nodeCounter, parameterEstimator, beliefEstimator, possibleDistributions);
 		}
 		nodeCounter++;
 		return node;

### 2012-12-08 src/eecs598/probability/ProbabilityUtil.java

@@ -41,7 +41,11 @@ public class ProbabilityUtil {
 		double sum = sum(values);
 		List<Double> normalizedValues = new ArrayList<Double>(values.size());
 		for(Double value : values) {
-			normalizedValues.add(value / sum);
+			if(sum > 0) {
+				normalizedValues.add(value / sum);
+			} else {
+				normalizedValues.add(0.5);
+			}
 		}
 		return normalizedValues;
 	}
@@ -53,7 +57,11 @@ public class ProbabilityUtil {
 	public static void normalizeToOne(HashMap<? extends Object, Double> values) {
 		double sum = sum(values.values());
 		for(Map.Entry<? extends Object, Double> entry : values.entrySet()) {
-			entry.setValue(entry.getValue() / sum);
+			if(sum > 0) {
+				entry.setValue(entry.getValue() / sum);
+			} else {
+				entry.setValue(0.5);
+			}
 		}
 	}
 	

### 2012-12-08 src/eecs598/test/ProbabilityUtilTest.java

@@ -47,5 +47,18 @@ public class ProbabilityUtilTest {
 			fail();
 		} catch(IllegalArgumentException e) {}
 	}
+	
+	@Test
+	public void normalizeToOneTest() {
+		HashMap<Double, Double> probMap = new HashMap<>();
+		probMap.put(1.0, 0.0);
+		probMap.put(2.0, 0.0);
+		
+		ProbabilityUtil.normalizeToOne(probMap);
+		
+		assertEquals(0.5, probMap.get(1.0), 0.000001);
+		assertEquals(0.5, probMap.get(2.0), 0.000001);
+		
+	}
 
 }

### 2012-12-08 src/eecs598/test/RandomDrawBeliefEstimatorTest.java

@@ -9,7 +9,9 @@ import java.util.List;
 import org.junit.Test;
 
 import eecs598.RandomDrawBeliefEstimator;
+import eecs598.experiments.DistributionRepository;
 import eecs598.factories.probability.DistributionFactory;
+import eecs598.factories.probability.GaussianFactory;
 import eecs598.probability.Distribution;
 import eecs598.test.helpers.TestDistributions;
 
@@ -42,9 +44,20 @@ public class RandomDrawBeliefEstimatorTest {
 		for(Double belief : beliefs.values()) {
 			assertEquals(expectedBelief, belief, 0.0001);
 		}
+	}
+	
+	@Test
+	public void testGaussian() {
+		//55.0506799730004
+		List<Distribution> possibleDistributions = new ArrayList<>();
+		DistributionRepository.getTwoGaussiansHard(possibleDistributions);
 		
+		RandomDrawBeliefEstimator estimator = new RandomDrawBeliefEstimator(new GaussianFactory());
+		HashMap<Double, Double> beliefs = estimator.estimateBeliefs(55.0506799730004, possibleDistributions);
 		
-		
+		for(Double belief : beliefs.values()) {
+			assertFalse(Double.isNaN(belief));
+		}
 	}
 
 }

### 2012-12-08 src/eecs598/DeGrootNode.java
Many many changes. Code's pretty messy.

@@ -1,8 +1,10 @@
 package eecs598;
 
+import java.io.Serializable;
 import java.util.Collection;
 import java.util.HashMap;
 import java.util.List;
+import java.util.Map;
 
 import eecs598.probability.Distribution;
 import eecs598.probability.ProbabilityUtil;
@@ -19,7 +21,12 @@ import eecs598.util.Util;
  * @author Pedro
  *
  */
-public class DeGrootNode extends Node {
+public class DeGrootNode extends Node implements Serializable {
+	
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = 1L;
 	
 	// TODO I am not considering the node's own estimate for the first time
 	// it receives a signal -- I am just copying the average of the neighbor's.
@@ -61,6 +68,10 @@ public class DeGrootNode extends Node {
 
 	@Override
 	public void newSignal(Collection<Node> neighbors, double signal) {
+		if(getId() == 5) {
+			// XXX
+			int a = 42;
+		}
 		//
 		// Use the signal to update our estimate.
 		//
@@ -86,15 +97,12 @@ public class DeGrootNode extends Node {
 		}
 		
 		for(Node neighbor : neighbors) {
-			//if(neighbor instanceof NonBayesianNode) {
-			// XXX test code!
 			double weight = getNeighborInfluence(neighbor, neighbors);
-			double weightedEstimate = weight * ProbabilityUtil.expectedValue(neighbor.getBeliefs());
+			Map<Double,Double> neighborsBeliefs = neighbor.getBeliefs();
+			double expectedValue = ProbabilityUtil.expectedValue(neighborsBeliefs);
+			double weightedEstimate = weight * expectedValue;
 			sumEstimates += weightedEstimate;
 			sumWeights += weight;
-			
-				
-			//}
 		}
 		
 		if(sumWeights > 0) {
@@ -122,8 +130,13 @@ public class DeGrootNode extends Node {
 		if(neighbors.contains(this)) {
 			throw new IllegalStateException("Self-loop in node " + toString() + ". Self-loops are not allowed.");
 		}
-		int neighborCount = neighbors.size() + 1; // +1 accounts for self-edge
-		return 1.0/neighborCount;		
+		if(neighbor instanceof NonBayesianNode) {
+			return 2;
+		} else {
+			return 1;
+		}
+//		int neighborCount = neighbors.size();// + 1; // +1 accounts for self-edge
+//		return 1.0/neighborCount;		
 	}
 
 

### 2012-12-08 src/eecs598/Edge.java

@@ -1,11 +1,17 @@
 package eecs598;
 
+import java.io.Serializable;
+
 /**
  * An edge connecting two nodes.
  * @author Pedro
  *
  */
-public class Edge {
+public class Edge implements Serializable {
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = 1L;
 	//
 	// Do we need anything fancier?
 	//

### 2012-12-08 src/eecs598/ManyRandomDrawsBeliefEstimator.java

@@ -10,6 +10,11 @@ import eecs598.util.Util;
 
 public class ManyRandomDrawsBeliefEstimator extends RandomDrawBeliefEstimator {
 
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = 1L;
+	
 	private final int numDraws = 50;
 	
 	public ManyRandomDrawsBeliefEstimator(

### 2012-12-08 src/eecs598/Node.java

@@ -1,12 +1,13 @@
 package eecs598;
 
+import java.io.Serializable;
 import java.util.Collection;
 import java.util.HashMap;
 import java.util.List;
 
 import eecs598.probability.Distribution;
 
-public abstract class Node {
+public abstract class Node implements Serializable {
 	
 	private int id;
 	

### 2012-12-08 src/eecs598/NonBayesianNode.java

@@ -1,5 +1,6 @@
 package eecs598;
 
+import java.io.Serializable;
 import java.util.ArrayList;
 import java.util.Collection;
 import java.util.HashMap;
@@ -10,7 +11,12 @@ import eecs598.probability.Distribution;
 import eecs598.probability.ProbabilityUtil;
 import eecs598.util.Util;
 
-public class NonBayesianNode extends Node {
+public class NonBayesianNode extends Node implements Serializable {
+
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = 1L;
 
 	/**
 	 * Associates each possible distribution to a belief between
@@ -29,7 +35,7 @@ public class NonBayesianNode extends Node {
 	}
 	
 	@Override
-	public void newSignal(Collection<Node> neighbors, double signal) {
+	public synchronized void newSignal(Collection<Node> neighbors, double signal) {
 		//
 		// Perform the bayesian update + the degroot-style averaging of neighbors.
 		//
@@ -141,7 +147,7 @@ public class NonBayesianNode extends Node {
 	}
 
 	@Override
-	public HashMap<Double, Double> getBeliefs() {
+	public synchronized HashMap<Double, Double> getBeliefs() {
 		/**
 		 * Returning a shallow copy should be fine -- I don't think we will update
 		 * the Doubles inside of the HashMap.

### 2012-12-08 src/eecs598/NopParameterEstimator.java

@@ -1,11 +1,18 @@
 package eecs598;
 
+import java.io.Serializable;
+
 /**
  * This class doesn't do anything with the new signal.
  * @author Pedro
  *
  */
-public class NopParameterEstimator implements ParameterEstimator {
+public class NopParameterEstimator implements ParameterEstimator, Serializable {
+
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = 1L;
 
 	@Override
 	public double estimateParameter(double signal, double currentEstimate) {

### 2012-12-08 src/eecs598/RandomDrawBeliefEstimator.java

@@ -1,5 +1,6 @@
 package eecs598;
 
+import java.io.Serializable;
 import java.util.HashMap;
 import java.util.List;
 
@@ -16,8 +17,12 @@ import eecs598.probability.ProbabilityUtil;
  * @author Pedro
  *
  */
-public class RandomDrawBeliefEstimator implements BeliefEstimator {
+public class RandomDrawBeliefEstimator implements BeliefEstimator, Serializable {
 	
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = 1L;
 	/**
 	 * This class creates parametrized distributions. We use it to construct
 	 * a customized distribution with our current estimate of the parameter.

### 2012-12-08 src/eecs598/experiments/ExperimentController.java

@@ -8,6 +8,7 @@ import edu.uci.ics.jung.graph.Graph;
 import eecs598.Edge;
 import eecs598.Node;
 import eecs598.experiments.analyzer.ExperimentAnalyzer;
+import eecs598.experiments.visualization.NetworkVisualizer;
 import eecs598.probability.Distribution;
 
 /**
@@ -28,7 +29,7 @@ public class ExperimentController {
 	public void attachAnalyzer(ExperimentAnalyzer analyzer) {
 		this.analyzers.add(analyzer);
 	}
-	
+
 	public void run(Graph<Node, Edge> graph, int numTimesteps) {
 		notifyAllAnalyzers(0, graph);
 		for(int i = 0; i < numTimesteps; i++) {

### 2012-12-08 src/eecs598/experiments/LoadGraph.java

@@ -1,0 +1,42 @@
+package eecs598.experiments;
+
+import java.io.FileInputStream;
+import java.io.IOException;
+import java.io.ObjectInputStream;
+
+import edu.uci.ics.jung.algorithms.layout.CircleLayout;
+import edu.uci.ics.jung.graph.DirectedSparseGraph;
+import edu.uci.ics.jung.graph.Graph;
+import edu.uci.ics.jung.graph.UndirectedGraph;
+import edu.uci.ics.jung.graph.UndirectedSparseGraph;
+import edu.uci.ics.jung.visualization.layout.PersistentLayoutImpl;
+import eecs598.Edge;
+import eecs598.ManyRandomDrawsBeliefEstimator;
+import eecs598.Node;
+import eecs598.experiments.visualization.NetworkVisualizer;
+import eecs598.probability.Gaussian;
+
+public class LoadGraph {
+	public static void main(String args[]) throws ClassNotFoundException, IOException {
+		FileInputStream underlyingStream2 = new FileInputStream( "no_convergence_85.jung" ); 
+		//FileInputStream underlyingStream2 = new FileInputStream( "no_conv_2.jung" );
+	    ObjectInputStream deserializer = new ObjectInputStream( underlyingStream2 );
+	    UndirectedSparseGraph<Node, Edge> loadedGraph = (UndirectedSparseGraph<Node, Edge>) deserializer.readObject(); //EXCEPTION THROWN HERE
+	    deserializer.close();
+	    underlyingStream2.close();
+	    
+	    NetworkVisualizer visualizer = new NetworkVisualizer();
+	    visualizer.showGraph(loadedGraph);
+	    
+	    ConvergenceInspector inspector = new ConvergenceInspector();
+	    System.out.println("Convergence before: " + inspector.haveConverged(loadedGraph.getVertices()));
+	    
+	    ExperimentController controller = new ExperimentController(new Gaussian(6.0));
+	    controller.run(loadedGraph, 500);
+	    visualizer.refresh();
+	    controller.run(loadedGraph, 1500);
+	    
+	    System.out.println("Convergence after: " + inspector.haveConverged(loadedGraph.getVertices()));
+	    //visualizer.showGraph(loadedGraph);
+	}
+}

### 2012-12-08 src/eecs598/experiments/RatioNonBayesianDeGroot.java

@@ -1,5 +1,8 @@
 package eecs598.experiments;
 
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.io.ObjectOutputStream;
 import java.util.ArrayList;
 import java.util.List;
 
@@ -52,15 +55,17 @@ public class RatioNonBayesianDeGroot {
 		
 		Graph<Node, Edge> graph = erdosRenyiGenerator.create();
 		
-		controller.run(graph, 300);
+		controller.run(graph, 5000);
 		
 		ConvergenceInspector convergenceInspector = new ConvergenceInspector();
 		boolean converged = convergenceInspector.haveConverged(graph.getVertices());
-		System.out.println("\tConvergence: " + converged);
-		if(converged) {
-			System.out.println("\tParameter: " + convergenceInspector.getConvergedParameter(graph.getVertices()));
+//		System.out.println("\tConvergence: " + converged);
+//		if(converged) {
+//			System.out.println("\tParameter: " + convergenceInspector.getConvergedParameter(graph.getVertices()));
+//		}
+		if(!converged) {
+			System.out.println("Did not converge");
 		}
-		
 		return graph;
 	}
 	
@@ -111,20 +116,42 @@ public class RatioNonBayesianDeGroot {
 		RatioNonBayesianDeGroot onlyNb = new RatioNonBayesianDeGroot(ratio, possibleDistributions, new GaussianFactory());
 		
 		ExperimentController controller = new ExperimentController(trueDistribution);
-		controller.attachAnalyzer(new AverageBeliefTracker(System.out, NodeType.NonBayesian));
-		controller.attachAnalyzer(new AverageBeliefTracker(System.err, NodeType.DeGroot));
+		//controller.attachAnalyzer(new AverageBeliefTracker(System.out, NodeType.NonBayesian));
+		//controller.attachAnalyzer(new AverageBeliefTracker(System.err, NodeType.DeGroot));
 		//controller.attachAnalyzer(new ParameterEstimateTracker(System.err));
 		
-		return onlyNb.runErdosRenyi(controller, 80, 0.1);
+		return onlyNb.runErdosRenyi(controller, 20, 0.1);
 	}
 	
-	public static void main(String[] args) {
+	public static void main(String[] args) throws IOException {
 		double ratio = 0.8;
 		//runSanityCheck(ratio);
 		//run2GaussiansEasy(ratio);
 		//Graph graph = run2GaussiansHard(ratio);
[…]

### 2012-12-08 src/eecs598/experiments/analyzer/AverageBeliefTracker.java

@@ -76,7 +76,8 @@ public class AverageBeliefTracker implements ExperimentAnalyzer {
 		StringBuilder logBlder = new StringBuilder();
 		logBlder.append(timestep).append("\t");
 		for(ParameterBeliefPair paramBelief : parameterBeliefs) {
-			logBlder.append(paramBelief.parameter).append("\t").append(paramBelief.belief).append("\t");
+			//logBlder.append(paramBelief.parameter).append("\t");
+			logBlder.append(paramBelief.belief).append("\t");
 		}
 		stream.println(logBlder.toString());
 	}

### 2012-12-08 src/eecs598/experiments/visualization/NetworkVisualizer.java

@@ -2,6 +2,7 @@ package eecs598.experiments.visualization;
 
 import java.awt.Dimension;
 import java.awt.Shape;
+import java.io.IOException;
 
 import javax.swing.JFrame;
 
@@ -9,29 +10,37 @@ import edu.uci.ics.jung.algorithms.layout.CircleLayout;
 import edu.uci.ics.jung.algorithms.layout.Layout;
 import edu.uci.ics.jung.graph.Graph;
 import edu.uci.ics.jung.visualization.BasicVisualizationServer;
+import edu.uci.ics.jung.visualization.layout.PersistentLayoutImpl;
 import eecs598.Node;
 import eecs598.Edge;
 
 public class NetworkVisualizer {
 	
+	private JFrame frame = null;
+	
 	public void showGraph(Graph<Node, Edge> graph) {
 		
 		Layout<Node, Edge> layout = new CircleLayout<>(graph);
 		layout.setSize(new Dimension(700,700)); // sets the initial size of the layout space
+
         // The BasicVisualizationServer<V,E> is parameterized by the vertex and edge types
 		
         BasicVisualizationServer<Node,Edge> vv = new BasicVisualizationServer<>(layout);
         vv.setPreferredSize(new Dimension(700,700)); //Sets the viewing area size
-        
         vv.getRenderContext().setVertexLabelTransformer(new Transformers.VertexLabel());
         vv.getRenderContext().setVertexShapeTransformer(new Transformers.VertexShape());
         //Shape s = vv.getRenderContext().getVertexShapeTransformer().transform(graph.getVertices().iterator().next());
         
-        JFrame frame = new JFrame("Kleinberg Test");
+        frame = new JFrame("Kleinberg Test");
         frame.setDefaultCloseOperation(JFrame.EXIT_ON_CLOSE);
         frame.getContentPane().add(vv); 
         frame.pack();
         frame.setVisible(true);       
+	}
+
+	public void refresh() {
+		frame.repaint();
+		
 	}
 	
 }

### 2012-12-08 src/eecs598/experiments/visualization/Transformers.java

@@ -45,9 +45,9 @@ public class Transformers {
 		@Override
 		public String transform(Node node) {
 			if(node instanceof NonBayesianNode) {
-				return String.format("%.2f", ProbabilityUtil.expectedValue(node.getBeliefs()));
+				return String.format("%d: %.2f", node.getId(), ProbabilityUtil.expectedValue(node.getBeliefs()));
 			} else {
-				return String.format("%.2f", ((DeGrootNode)node).getParameterEstimate());
+				return String.format("%d: %.2f", node.getId(), ((DeGrootNode)node).getParameterEstimate());
 			}
 		}
 	}

### 2012-12-08 src/eecs598/factories/probability/GaussianFactory.java

@@ -1,9 +1,11 @@
 package eecs598.factories.probability;
 
+import java.io.Serializable;
+
 import eecs598.probability.Distribution;
 import eecs598.probability.Gaussian;
 
-public class GaussianFactory implements DistributionFactory {
+public class GaussianFactory implements DistributionFactory, Serializable {
 
 	@Override
 	public Distribution create(double mean) {

### 2012-12-08 src/eecs598/probability/Gaussian.java

@@ -1,9 +1,11 @@
 package eecs598.probability;
 
+import java.io.Serializable;
+
 import cern.jet.random.Normal;
 import cern.jet.random.engine.RandomEngine;
 
-public class Gaussian implements Distribution {
+public class Gaussian implements Distribution, Serializable {
 
 	private Normal normal;
 	private double mean;

### 2012-12-08 src/eecs598/probability/ProbabilityUtil.java

@@ -19,9 +19,9 @@ public class ProbabilityUtil {
 	 * Performs sum(probabilityMap[i].key * probabilityMap[i].value) for all valid i.
 	 * @return
 	 */
-	public static double expectedValue(HashMap<Double, Double> probabilityMap) {
+	public static double expectedValue(Map<Double, Double> neighborsBeliefs) {
 		double expectedValue = 0;
-		for(Map.Entry<Double, Double> valueProbPair : probabilityMap.entrySet()) {
+		for(Map.Entry<Double, Double> valueProbPair : neighborsBeliefs.entrySet()) {
 			double variableValue = valueProbPair.getKey();
 			double probability = valueProbPair.getValue();
 			if(probability >= 0 && probability <= 1) {

### 2012-12-08 docs/paper.tex
Added discussion of convergence

@@
 
+\subsection{Convergence}
+In this section we discuss theoretical results concerning convergence.
+Here we define convergence as consisting of two parts: convergence for Non-Bayesian nodes and convergence for DeGroot nodes.
+For a Non-Bayesian node $b$, we consider $b$ to have converged to a belief state $\theta_{k}$ if $\mu_{b,t}(\theta_k) \to 1$ as $t \to \infty$.
+We consider a DeGroot node $d$ to have converged to the belief value $m$ if $m_{d,t} \to m$ as $t \to \infty$.
+If these conditions hold for every Non-Bayesian and DeGroot node in the network, we consider the network to have converged.
+
+We will demonstrate that convergence occurs for a very simple instance of our model, and then discuss difficulties encountered when attempting to extend these results.
+
+\subsubsection{Convergence in a Simple Case}
+Consider a network consisting of a Non-Bayesian node $b$ and a DeGroot node $d$ where $b$ and $d$ are connected and $d$ has a nonzero prior on the true state.
+Suppose that $a_{dd}$ and $a_{bd}$ are strictly positive but that $a_{db} = 0$.
+That is, the DeGroot node listens to the Non-Bayesian node but the Non-Bayesian does not consider the belief of the DeGroot node.
+
+The update calculation for the Non-Bayesian node will then be 
+\begin{equation}
+\mu_{b,t+1}(\theta_k) = a_{bb}\mu_{b,t}(\theta_k)\frac{\ell_i(\omega_{b,t+1}|\theta_k)}{m_{b,t}(\omega_{b,t+1})}
+\end{equation}
+
+This is simply a Bayesian update based on $b$'s signal received at every timestep, so follows that $b$'s belief will converge to the correct value.
+That is, $\mu_{b,t}(\theta^*) \to 1$ as $t \to \infty$ where $\theta^*$ is the correct belief state.
+
+The DeGroot node $d$'s update calculation will be
+\begin{equation}
+m_{d,t+1} = a_{db}\sum_{i=1}^n\mu_{d,t}(\theta_i)\hat{m_k}
+\end{equation}
+
+Once $b$ has converged to the correct state this will reduce to
+
+\begin{equation}
+m_{d,t+1} = a_{db}\hat{m_{\theta^*}} = m^*
+\end{equation}
+
+Thus we observe that the network consisting of a DeGroot node listening to a Non-Bayesian node will converge to the correct belief.
+
+\subsubsection{Difficulties in Extending Convergence Results}
+Consider the simple network described in the previous section with the modification that $a_{bd}$ is strictly positive, so that the Non-Bayesian node takes into account the belief of the DeGroot node.
+We then have
+
+\begin{equation}
+\mu_{b,t+1} = a_{bb}\mu_{b,t}(\theta_w)\frac{\ell_i(\omega_{b,t+1}|\theta_k)}{m_{b,t}(\omega_{b,t+1})} + a_{bd}\mu_{d,t}^\prime(\theta_w)
+\end{equation}
+where the term $\mu_{d,t}^\prime(\theta_w)$ depends on the method used to convert DeGroot to Non-Bayesian belief.
+The methods we consider in sections \ref{sec:draw_from_degroot} and \ref{sec:likelihood_metric} both inject a level of noise into the network during each belief update through this term.
+
+Noise from section~\ref{sec:draw_from_degroot}'s method results from the fact that we are performing a random draw from a probability distribution $p_{j,t}$ created from the parameter $m_{j,t}$ which may be different from the true value $m^*$.
+Even if many draws are performs and averaged so that the ``signal-to-noise'' ratio is increased, the inclusion of data from a potentially incorrect probability distribution will still inject error into the network.
+
+The likelihood metric method discussed in section~\ref{sec:likelihood_metric} also introduces error.
+Even if the DeGroot node $d$'s belief $m_{d,t}$ has converged to the correct value $m^*$, we still have
+\begin{equation}
+\mu_{d,t}^\prime(\theta_w) \propto e^{-(m_{d,t} - \hat{m_w})^2} > 0
+\end{equation}
+for each incorrect state $\{ \theta_w \in \Theta : \theta_w \neq \theta^* \}$.  This will result in a small amount of noise added to each update of $d$'s neighbors' beliefs.
+
+We have observed in simulation that the noise from the DeGroot to Non-Bayesian conversion can overcome the rate of learning from the signal observations and thus prevent convergence of the network.
+However, it is difficult to determine exactly what conditions must hold for this to be the case.
+The level of impact from the conversion noise will depend on many factors including network structure, trust values between nodes, and the number of states $\theta_i \in \Theta$ used to quantize possible values of $m^*$.
+We have therefore found it difficult to prove convergence results with any significant level of generality.
+
+% Can discuss in conclusion that future work could either focus on figuring out how to do this or on developing other ways of doing the DeGroot-to-Non-Bayesian conversion that make such proofs easier.
+
 \bibliographystyle{plain}

### 2012-12-09 docs/paper.tex
Added introduction/background section

@@
 
-\section{Introduction}
+\section{Introduction and Background}
 
-\cite{Jadbabaie2012}
-\cite{DeGroot1974}
+Social learning is a process that occurs in a tremendous variety of settings; individuals and groups attempt to develop correct beliefs about complex issues such as economic patterns, social trends, and on new developments in technology.
+Information may not always be easy to obtain in these situations.
+Individuals receive a very limited picture of the true state of the world, and therefore must turn to neighbors in a social network to share opinions about these observations.
+Thus we can think of the network as a whole attempting to learn the true state.
+
+Many attempts have been made to model this phenomenon.
+The DeGroot model of social influence proposes a system for reaching consensus where each node in a network adjusts their belief over time by linear combinations of their neighbors' beliefs~\cite{DeGroot1974}.
+More sophisticated learning methods such as Bayesian inference provide algorithms for combining observations, neighboring opinions, and knowledge about network structure with prior beliefs to create a probability distribution over different belief states.
+Jadbabaie et.
+al.
+propose a model for social learning that combines a Bayesian-style update with a simple linear inclusion of neighbors' opinions~\cite{Jadbabaie2012}.
+They show that convergence to the correct belief about the state of the world is guaranteed under some straightforward assumptions about network connectivity and prior beliefs.
+
+We seek to investigate the behavior of a network consisting of nodes learning in the ``Non-Bayesian'' style of Jadbabaie et.
+al.
+with the added presence of DeGroot-style nodes.
+These DeGroot nodes will make no observations about the state of the world and incorporate neighboring beliefs in a simple linear manner.
+This can model social learning scenarios where some members of a network thoughtfully develop beliefs based on observations and advice, and others do nothing but naively pass along opinions.
+What are the consequences of such naive agents in a social learning scenario?
+Do certain network structures exacerbate their impact?
+How many naive agents can be present before learning becomes prohibitively difficult?
+In this work we investigate answers to these questions and propose our model of mixed Non-Bayesian and DeGroot learning as a tool for future research.
 
@@
 $\mathbb{P}$ is a pre-defined class of distributions where each  $p^*(t) \in \mathbb{P}$ is distinguishable by a single parameter.
-This single parameter $m^*$ where $\{m^* \in \mathbb{R}: m_{min} <= m^* <= m_{max} \}$  will be the state which the nodes in the network are attempting to learn.
+This single parameter $m^*$ where $\{m^* \in \mathbb{R}: m_{min} <= m^* <= m_{max} \}$  will be the state that the nodes in the network are attempting to learn.
 That is, $m^*$ is the ``true'' state of the world.
@@
 Examples include the Poisson distribution with parameter $m^*$ and Gaussian distribution with mean $m^*$ and constant variance.
-We also introduce a trapezoidal probability distribution in section~\ref{sec:trapezoidal_distribution} which serves as a valid choice for $\mathbb{P}$.
+We also introduce a trapezoidal probability distribution in section~\ref{sec:trapezoidal_distribution} that serves as a valid choice for $\mathbb{P}$.
 
-At each timestep $t$, every Non-Bayesian node $i$ will receive a signal $s_{i,t}$ which is a value drawn from $p^*(x)$.
+At each timestep $t$, every Non-Bayesian node $i$ will receive a signal $s_{i,t}$ that is a value drawn from $p^*(x)$.
 These observations will be used by the nodes in the network to construct a belief about $m^*$.
@@
 
-As an example of a class of distributions which can be used in our model we present the following trapezoidal distribution.
+As an example of a class of distributions that can be used in our model we present the following trapezoidal distribution.
 
@@
 
-We require a method for converting a DeGroot node $j$'s belief $m_{j,t} \in \mathbb{R}$ to a series of priors which can be included in a Non-Bayesian node $i$'s belief update.
+We require a method for converting a DeGroot node $j$'s belief $m_{j,t} \in \mathbb{R}$ to a series of priors that can be included in a Non-Bayesian node $i$'s belief update.
 The first method we consider involves generating a probability distribution $p_{j,t}$ from $j$'s belief at time $t$ and drawing from this distribution.
@@
 
-This is simply the distribution which $j$ believes to be the state of the world.
+This is simply the distribution that $j$ believes to be the state of the world.
 We then draw a single signal $s_{j,t}^\prime$ from this distribution.
@@
 \end{equation}
-where $\mu_{j,t}^\prime$ is the belief distribution which is used for the DeGroot node $j$'s values of $\mu_{j,t}(\theta_k)$ in the Non-Bayesian update of equation~\ref{eq:non_bayesian_update}.
+where $\mu_{j,t}^\prime$ is the belief distribution that is used for the DeGroot node $j$'s values of $\mu_{j,t}(\theta_k)$ in the Non-Bayesian update of equation~\ref{eq:non_bayesian_update}.
 
@@
 
-Noise from section~\ref{sec:draw_from_degroot}'s method results from the fact that we are performing a random draw from a probability distribution $p_{j,t}$ created from the parameter $m_{j,t}$ which may be different from the true value $m^*$.
+Noise from section~\ref{sec:draw_from_degroot}'s method results from the fact that we are performing a random draw from a probability distribution $p_{j,t}$ created from the parameter $m_{j,t}$ that may be different from the true value $m^*$.
 Even if many draws are performs and averaged so that the ``signal-to-noise'' ratio is increased, the inclusion of data from a potentially incorrect probability distribution will still inject error into the network.

### 2012-12-09 docs/paper.tex
Brief section on network structure

@@
 
-(Mixed Non-Bayesian and DeGroot nodes)
+The network in our model consists of an undirected graph where each vertex is either a Non-Bayesian or a DeGroot node.
+At each discrete timestep $t$, every node will perform a belief update of its corresponding type.
+If two vertices are connected by an edge, they are said to be neighbors and will incorporate each others' beliefs in their respective updates.
+
+The model allows for a variety of generative methods to be used for creation of the network structure such as Erdos-Renyi, Watts-Strogatz, Kleinberg's Small-World Model, or a power law distribution.
+We investigate each of these network types in section \{ \}.% @todo[DDC] Refer to simulation results
 

### 2012-12-09 docs/paper.tex
Added abstract

@@
 \maketitle
+
+\begin{abstract}
+We consider a model of social learning in which the network consists of two distinct types of agents: nodes following the Non-Bayesian update rule developed by Jadbabaie et.
+al.
+are interspersed with non-observant nodes performing simple DeGroot-style belief updates.
+We develop a model that allows these types of update rules to coexist, and we consider implications on belief convergence.
+We present simulations of our model for a variety of network structures and ratios of Non-Bayesian to DeGroot nodes.
+\end{abstract}
 
@@
 
-\subsection{Convergence}
+\section{Convergence}
 In this section we discuss theoretical results concerning convergence.
@@
 
-\subsubsection{Convergence in a Simple Case}
+\subsection{Convergence in a Simple Case}
 Consider a network consisting of a Non-Bayesian node $b$ and a DeGroot node $d$ where $b$ and $d$ are connected and $d$ has a nonzero prior on the true state.
@@
 
-\subsubsection{Difficulties in Extending Convergence Results}
+\subsection{Difficulties in Extending Convergence Results}
 Consider the simple network described in the previous section with the modification that $a_{bd}$ is strictly positive, so that the Non-Bayesian node takes into account the belief of the DeGroot node.
@@
 
+\section{Conclusion}
+
 % Can discuss in conclusion that future work could either focus on figuring out how to do this or on developing other ways of doing the DeGroot-to-Non-Bayesian conversion that make such proofs easier.

### 2012-12-09 src/eecs598/experiments/ConvergenceInspector.java
Convergence time test; several small changes.

@@ -17,7 +17,7 @@ import eecs598.util.DoubleEquals;
  */
 public class ConvergenceInspector {
 	
-	private final double beliefConvergenceThreshold = 0.00001;
+	private final double beliefConvergenceThreshold = 0.0001;
 	
 	/**
 	 * We define convergence as:

### 2012-12-09 src/eecs598/experiments/ConvergenceStressTest.java

@@ -1,0 +1,121 @@
+package eecs598.experiments;
+
+import java.io.FileNotFoundException;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.io.ObjectOutputStream;
+import java.util.Date;
+
+import org.apache.commons.collections15.Factory;
+
+import edu.uci.ics.jung.algorithms.generators.GraphGenerator;
+import edu.uci.ics.jung.graph.Graph;
+import edu.uci.ics.jung.graph.UndirectedGraph;
+import eecs598.Edge;
+import eecs598.ManyRandomDrawsBeliefEstimator;
+import eecs598.Node;
+import eecs598.NopParameterEstimator;
+import eecs598.experiments.visualization.NetworkVisualizer;
+import eecs598.factories.EdgeFactory;
+import eecs598.factories.GraphFactory;
+import eecs598.factories.RatioNodeFactory;
+
+public class ConvergenceStressTest {
+	
+	private double ratioNonBayesian = 0.8;
+	private GeneratorFactory generatorFactory;
+	private int convergenceTestGranularity = 20;
+	private int maxTimesteps = 500;
+	
+	public double getRatioNonBayesian() {
+		return ratioNonBayesian;
+	}
+
+	public void setRatioNonBayesian(double ratioNonBayesian) {
+		this.ratioNonBayesian = ratioNonBayesian;
+	}
+
+	public GeneratorFactory getGeneratorFactory() {
+		return generatorFactory;
+	}
+
+	public void setGeneratorFactory(GeneratorFactory generatorFactory) {
+		this.generatorFactory = generatorFactory;
+	}
+
+	public int getConvergenceTestGranularity() {
+		return convergenceTestGranularity;
+	}
+
+	public void setConvergenceTestGranularity(int convergenceTestGranularity) {
+		this.convergenceTestGranularity = convergenceTestGranularity;
+	}
+
+	public int getMaxTimesteps() {
+		return maxTimesteps;
+	}
+
+	public void setMaxTimesteps(int maxTimesteps) {
+		this.maxTimesteps = maxTimesteps;
+	}
+
+	public void run(int nRuns, Factory<ExperimentalSetup> setupFactory) throws IOException {
+		for(int i = 0; i < nRuns; i++) {
+			ExperimentalSetup setup = setupFactory.create();
+			Experiment experiment = new Experiment(setup);
+			experiment.setConvergenceTestStep(convergenceTestGranularity);
[…]

### 2012-12-09 src/eecs598/experiments/ConvergenceTimeTest.java

@@ -1,0 +1,129 @@
+package eecs598.experiments;
+
+import java.io.FileNotFoundException;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.io.ObjectOutputStream;
+import java.util.ArrayList;
+import java.util.Date;
+import java.util.List;
+
+import org.apache.commons.collections15.Factory;
+
+import edu.uci.ics.jung.algorithms.generators.GraphGenerator;
+import edu.uci.ics.jung.graph.Graph;
+import edu.uci.ics.jung.graph.UndirectedGraph;
+import eecs598.Edge;
+import eecs598.ManyRandomDrawsBeliefEstimator;
+import eecs598.Node;
+import eecs598.NopParameterEstimator;
+import eecs598.experiments.visualization.NetworkVisualizer;
+import eecs598.factories.EdgeFactory;
+import eecs598.factories.GraphFactory;
+import eecs598.factories.RatioNodeFactory;
+import eecs598.util.MeanAndStdDev;
+
+public class ConvergenceTimeTest {
+	private double ratioNonBayesian = 0.8;
+	private GeneratorFactory generatorFactory;
+	private int convergenceTestGranularity = 20;
+	private int maxTimesteps = 500;
+	
+	public double getRatioNonBayesian() {
+		return ratioNonBayesian;
+	}
+
+	public void setRatioNonBayesian(double ratioNonBayesian) {
+		this.ratioNonBayesian = ratioNonBayesian;
+	}
+
+	public GeneratorFactory getGeneratorFactory() {
+		return generatorFactory;
+	}
+
+	public void setGeneratorFactory(GeneratorFactory generatorFactory) {
+		this.generatorFactory = generatorFactory;
+	}
+
+	public int getConvergenceTestGranularity() {
+		return convergenceTestGranularity;
+	}
+
+	public void setConvergenceTestGranularity(int convergenceTestGranularity) {
+		this.convergenceTestGranularity = convergenceTestGranularity;
+	}
+
+	public int getMaxTimesteps() {
+		return maxTimesteps;
+	}
+
+	public void setMaxTimesteps(int maxTimesteps) {
+		this.maxTimesteps = maxTimesteps;
+	}
+
+	/**
+	 * Returns the average time to convergence.
+	 * @param nRuns
+	 * @param setupFactory
+	 * @return
+	 * @throws IOException
+	 */
[…]

### 2012-12-09 src/eecs598/experiments/DistributionRepository.java

@@ -75,10 +75,10 @@ public class DistributionRepository {
 	
 	public static Distribution getNGaussiansHard(int n, List<Distribution> possibleDistributions) {
 		throwIfNotEmpty(possibleDistributions);
-		double startingMean = 5.0;
+		double startingMean = 100.0;
 		double step = 1;
 		for(int i = 0; i < n; i++) {
-			possibleDistributions.add(new Gaussian(startingMean += i*step));
+			possibleDistributions.add(new Gaussian(startingMean + i*step));
 		}
 		
 		return chooseRandom(possibleDistributions);

### 2012-12-09 src/eecs598/experiments/Experiment.java

@@ -1,0 +1,95 @@
+package eecs598.experiments;
+
+import org.apache.commons.collections15.Factory;
+
+import edu.uci.ics.jung.algorithms.generators.GraphGenerator;
+import edu.uci.ics.jung.graph.Graph;
+import edu.uci.ics.jung.graph.UndirectedGraph;
+import eecs598.Edge;
+import eecs598.Node;
+
+/**
+ * 
+ * @author Pedro
+ *
+ */
+public class Experiment {
+	private ExperimentController experimentController;
+	
+	private int maxConvergenceTimesteps = 10000;
+	
+
+	/**
+	 * In runUntilConvergence, test for convergence every convergenceTestStep steps.
+	 */
+	private int convergenceTestStep = 10;
+
+	
+	public Experiment(ExperimentalSetup setup) {
+		super();
+		this.experimentController = new ExperimentController(setup.getTrueDistribution());
+	}
+
+	public Graph<Node, Edge> run(GeneratorFactory generatorFactory, Factory<Node> nodeFactory,
+			Factory<Edge> edgeFactory, Factory<UndirectedGraph<Node, Edge>> graphFactory, int numTimesteps) {
+		GraphGenerator<Node, Edge> generator = generatorFactory.create(nodeFactory, edgeFactory, graphFactory);
+		Graph<Node, Edge> graph = generator.create();
+		return run(graph, numTimesteps);
+	}
+
+	public Graph<Node, Edge> run(Graph<Node, Edge> graph, int numTimesteps) {
+		getExperimentController().run(graph, numTimesteps);
+		return graph;
+	}
+
+	/**
+	 * Runs the experiment until the graph converges, or throws an exception if the graph didn't converge before
+	 * maxConvergenceTimesteps.
+	 * @param generatorFactory
+	 * @param controller
+	 * @return the number of times steps, approximately.
+	 * @throws MaxTimestepsExceededException 
+	 */
+	public int runUntilConvergence(GeneratorFactory generatorFactory, Factory<Node> nodeFactory,
+			Factory<Edge> edgeFactory, Factory<UndirectedGraph<Node, Edge>> graphFactory)
+					throws MaxTimestepsExceededException {
+		GraphGenerator<Node, Edge> generator = generatorFactory.create(nodeFactory, edgeFactory, graphFactory);
+		Graph<Node, Edge> graph = generator.create();
+		return runUntilConvergence(graph);
+	}
+
[…]

### 2012-12-09 src/eecs598/experiments/ExperimentalSetup.java

@@ -1,0 +1,53 @@
+package eecs598.experiments;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import org.apache.commons.collections15.Factory;
+
+import eecs598.BeliefEstimator;
+import eecs598.ManyRandomDrawsBeliefEstimator;
+import eecs598.factories.probability.DistributionFactory;
+import eecs598.factories.probability.GaussianFactory;
+import eecs598.probability.Distribution;
+
+public class ExperimentalSetup {
+	private List<Distribution> possibleDistributions;
+	private Distribution trueDistribution;
+	private DistributionFactory distributionFactory;
+	
+	public ExperimentalSetup(List<Distribution> possibleDistributions,
+			Distribution trueDistribution,
+			DistributionFactory distributionFactory) {
+		super();
+		this.possibleDistributions = possibleDistributions;
+		this.trueDistribution = trueDistribution;
+		this.distributionFactory = distributionFactory;
+	}
+
+	public List<Distribution> getPossibleDistributions() {
+		return possibleDistributions;
+	}
+	
+	public Distribution getTrueDistribution() {
+		return trueDistribution;
+	}
+	
+	public DistributionFactory getDistributionFactory() {
+		return distributionFactory;
+	}
+
+	public static Factory<ExperimentalSetup> nGaussiansHardFactory(final int nGaussians) {
+		return new Factory<ExperimentalSetup>() {
+			@Override
+			public ExperimentalSetup create() {
+				List<Distribution> possibleDistributions = new ArrayList<Distribution>();
+				Distribution trueDistribution = DistributionRepository.getNGaussiansHard(nGaussians, possibleDistributions);
+				ExperimentalSetup setup = new ExperimentalSetup(possibleDistributions, trueDistribution, new GaussianFactory());
+				return setup;
+			}
+			
+		};
+		
+	}
+}

### 2012-12-09 src/eecs598/experiments/GeneratorFactories.java

@@ -1,0 +1,32 @@
+package eecs598.experiments;
+
+import org.apache.commons.collections15.Factory;
+
+import edu.uci.ics.jung.algorithms.generators.GraphGenerator;
+import edu.uci.ics.jung.algorithms.generators.random.KleinbergSmallWorldGenerator;
+import edu.uci.ics.jung.graph.UndirectedGraph;
+import eecs598.Edge;
+import eecs598.Node;
+
+public class GeneratorFactories {
+	public static class KleinbergGenerator implements GeneratorFactory {
+		private int latticeSize;
+		private double clusteringExponent;
+		
+		public KleinbergGenerator(int latticeSize, double clusteringExponent) {
+			super();
+			this.latticeSize = latticeSize;
+			this.clusteringExponent = clusteringExponent;
+		}
+
+
+
+		@Override
+		public GraphGenerator<Node, Edge> create(Factory<Node> nodeFactory,
+				Factory<Edge> edgeFactory,
+				Factory<UndirectedGraph<Node, Edge>> graphFactory) {
+			return new KleinbergSmallWorldGenerator<>(graphFactory, nodeFactory, edgeFactory, latticeSize, clusteringExponent);
+		}
+		
+	}
+}

### 2012-12-09 src/eecs598/experiments/GeneratorFactory.java

@@ -1,0 +1,13 @@
+package eecs598.experiments;
+
+import org.apache.commons.collections15.Factory;
+
+import edu.uci.ics.jung.algorithms.generators.GraphGenerator;
+import edu.uci.ics.jung.graph.UndirectedGraph;
+import eecs598.Edge;
+import eecs598.Node;
+
+public interface GeneratorFactory {
+	public GraphGenerator<Node, Edge> create(Factory<Node> nodeFactory, Factory<Edge> edgeFactory,
+			Factory<UndirectedGraph<Node, Edge>> graphFactory);
+}

### 2012-12-09 src/eecs598/experiments/LoadGraph.java

@@ -4,21 +4,15 @@ import java.io.FileInputStream;
 import java.io.IOException;
 import java.io.ObjectInputStream;
 
-import edu.uci.ics.jung.algorithms.layout.CircleLayout;
-import edu.uci.ics.jung.graph.DirectedSparseGraph;
-import edu.uci.ics.jung.graph.Graph;
-import edu.uci.ics.jung.graph.UndirectedGraph;
 import edu.uci.ics.jung.graph.UndirectedSparseGraph;
-import edu.uci.ics.jung.visualization.layout.PersistentLayoutImpl;
 import eecs598.Edge;
-import eecs598.ManyRandomDrawsBeliefEstimator;
 import eecs598.Node;
 import eecs598.experiments.visualization.NetworkVisualizer;
 import eecs598.probability.Gaussian;
 
 public class LoadGraph {
 	public static void main(String args[]) throws ClassNotFoundException, IOException {
-		FileInputStream underlyingStream2 = new FileInputStream( "no_convergence_85.jung" ); 
+		FileInputStream underlyingStream2 = new FileInputStream( "no_convergence_1355087145091.jung" ); 
 		//FileInputStream underlyingStream2 = new FileInputStream( "no_conv_2.jung" );
 	    ObjectInputStream deserializer = new ObjectInputStream( underlyingStream2 );
 	    UndirectedSparseGraph<Node, Edge> loadedGraph = (UndirectedSparseGraph<Node, Edge>) deserializer.readObject(); //EXCEPTION THROWN HERE
@@ -31,10 +25,10 @@ public class LoadGraph {
 	    ConvergenceInspector inspector = new ConvergenceInspector();
 	    System.out.println("Convergence before: " + inspector.haveConverged(loadedGraph.getVertices()));
 	    
-	    ExperimentController controller = new ExperimentController(new Gaussian(6.0));
-	    controller.run(loadedGraph, 500);
+	    ExperimentController controller = new ExperimentController(new Gaussian(80.0));
+	    controller.run(loadedGraph, 400);
 	    visualizer.refresh();
-	    controller.run(loadedGraph, 1500);
+	    //controller.run(loadedGraph, 1500);
 	    
 	    System.out.println("Convergence after: " + inspector.haveConverged(loadedGraph.getVertices()));
 	    //visualizer.showGraph(loadedGraph);

### 2012-12-09 src/eecs598/experiments/MaxTimestepsExceededException.java

@@ -1,0 +1,6 @@
+package eecs598.experiments;
+
+@SuppressWarnings("serial")
+public class MaxTimestepsExceededException extends Exception {
+
+}

### 2012-12-09 src/eecs598/util/MeanAndStdDev.java

@@ -1,0 +1,40 @@
+package eecs598.util;
+
+import java.util.Collection;
+
+public class MeanAndStdDev {
+	private double mean;
+	private double stdDev;
+	public MeanAndStdDev(double mean, double stdDev) {
+		super();
+		this.mean = mean;
+		this.stdDev = stdDev;
+	}
+	public double getMean() {
+		return mean;
+	}
+	public void setMean(double mean) {
+		this.mean = mean;
+	}
+	public double getStdDev() {
+		return stdDev;
+	}
+	public void setStdDev(double stdDev) {
+		this.stdDev = stdDev;
+	}
+	
+	public static MeanAndStdDev fromSample(Collection<Double> samples) {
+		double mean = 0.0;
+		for(Double sample : samples) {
+			mean += sample;
+		}
+		mean /= samples.size();
+		double variance = 0.0;
+		for(Double sample : samples) {
+			variance += Math.pow(sample - mean, 2);
+		}
+		double stdDev = Math.sqrt(variance/samples.size());
+		return new MeanAndStdDev(mean, stdDev);
+	}
+}
+

### 2012-12-10 src/eecs598/experiments/ConvergenceTimeTest.java
aosidhoasdhasiudh

@@ -13,9 +13,11 @@ import org.apache.commons.collections15.Factory;
 import edu.uci.ics.jung.algorithms.generators.GraphGenerator;
 import edu.uci.ics.jung.graph.Graph;
 import edu.uci.ics.jung.graph.UndirectedGraph;
+import eecs598.DistanceBeliefEstimator;
 import eecs598.Edge;
 import eecs598.ManyRandomDrawsBeliefEstimator;
 import eecs598.Node;
+import eecs598.NonBayesianNode;
 import eecs598.NopParameterEstimator;
 import eecs598.experiments.visualization.NetworkVisualizer;
 import eecs598.factories.EdgeFactory;
@@ -69,6 +71,9 @@ public class ConvergenceTimeTest {
 	 * @throws IOException
 	 */
 	public MeanAndStdDev run(int nRuns, Factory<ExperimentalSetup> setupFactory) throws IOException {
+		
+		NonBayesianNode.listensToSignalRatio = 0.4;
+		
 		List<Double> convergenceTimes = new ArrayList<Double>();
 		ExperimentalSetup setup = setupFactory.create();
 		Experiment experiment = new Experiment(setup);
@@ -79,7 +84,8 @@ public class ConvergenceTimeTest {
 				ratioNonBayesian,
 				setup.getPossibleDistributions(),
 				new NopParameterEstimator(),
-				new ManyRandomDrawsBeliefEstimator(setup.getDistributionFactory()));
+				//new ManyRandomDrawsBeliefEstimator(setup.getDistributionFactory()));
+				new DistanceBeliefEstimator());
 		
 		Factory<Edge> edgeFactory = new EdgeFactory();
 		
@@ -93,14 +99,17 @@ public class ConvergenceTimeTest {
 			connector.makeConnected(graph, edgeFactory);
 			if(!connector.isConnected(graph)) throw new RuntimeException("Graph is not connected!");
 			try {				
-				int timesteps = experiment.runUntilConvergence(
-						generatorFactory, nodeFactory, edgeFactory, graphFactory);
+				int timesteps = experiment.runUntilConvergence(graph);
 				//System.out.println(timesteps);
 				convergenceTimes.add((double)timesteps);
-				if(graph.getVertexCount() == 375) {
-					throw new MaxTimestepsExceededException();
-				}
 			} catch(MaxTimestepsExceededException e) {
+				//experiment.run(graph, 1);
+				try {
[…]

### 2012-12-10 src/eecs598/experiments/RatioNonBayesianDeGroot.java
Broken RatioNonBayesianDegroot

@@ -13,6 +13,7 @@ import edu.uci.ics.jung.graph.Graph;
 import edu.uci.ics.jung.graph.UndirectedGraph;
 import eecs598.Edge;
 import eecs598.ManyRandomDrawsBeliefEstimator;
+import eecs598.DistanceBeliefEstimator;
 import eecs598.Node;
 import eecs598.NopParameterEstimator;
 import eecs598.RandomDrawBeliefEstimator;
@@ -46,16 +47,19 @@ public class RatioNonBayesianDeGroot {
 		this.possibleDistributions = possibleDistributions;
 		this.nodeFactory = new RatioNodeFactory(
 				ratioNonBayesian, possibleDistributions,
-				new NopParameterEstimator(), new ManyRandomDrawsBeliefEstimator(distributionFactory));
+				new NopParameterEstimator(), new DistanceBeliefEstimator()/*new ManyRandomDrawsBeliefEstimator(distributionFactory)*/);
 		this.edgeFactory = new EdgeFactory();
 		this.graphFactory = new GraphFactory();
 	}
 
-	public Graph<Node, Edge> runErdosRenyi(ExperimentController controller, int numVertices, double p) {
+	public Graph<Node, Edge> runExperiment(ExperimentController controller, int numVertices, double p) {
 		ErdosRenyiGenerator<Node, Edge> erdosRenyiGenerator = new ErdosRenyiGenerator<Node, Edge>(
 				graphFactory, nodeFactory, edgeFactory, numVertices, p);
 		
-		Graph<Node, Edge> graph = erdosRenyiGenerator.create();
+                //		Graph<Node, Edge> graph = erdosRenyiGenerator.create();
+                Graph<Node, Edge> graph = new GeneratorFactories.ErdosRenyiFactory(15, 1.0).create(nodeFactory, edgeFactory, graphFactory).create();
+                GraphConnector connector = new GraphConnector();
+                connector.makeConnected(graph, edgeFactory);
 		
                 final int numTimesteps = 2000;
 		//controller.run(graph, numTimesteps);
@@ -80,7 +84,7 @@ public class RatioNonBayesianDeGroot {
 		Distribution trueDistribution = DistributionRepository.getZeroAndUniform(uniformId, possibleDistributions);
 		RatioNonBayesianDeGroot onlyNb = new RatioNonBayesianDeGroot(ratio, possibleDistributions, new GaussianFactory());
 		
[…]

### 2012-12-11 src/eecs598/DeGrootNode.java
Ratio of nodes w/ distance metric

@@ -135,7 +135,7 @@ public class DeGrootNode extends Node implements Serializable {
 			return 0;
 		}
 		if(neighbor instanceof NonBayesianNode) {
-			return 2;
+			return 1;
 		} else {
 			return 1;
 		}

### 2012-12-11 src/eecs598/experiments/RatioNonBayesianDeGroot.java

@@ -118,7 +118,7 @@ public class RatioNonBayesianDeGroot {
 	
 	public static Graph<Node, Edge> runNGaussiansHard(int n, double ratio) {
 		List<Distribution> possibleDistributions = new ArrayList<>();
-		Distribution trueDistribution = DistributionRepository.getNGaussiansHard(n, possibleDistributions);
+		Distribution trueDistribution = DistributionRepository.getNGaussiansMedium(2, possibleDistributions);
 		//System.out.println(n + " Gaussians Hard: True mean = " + trueDistribution.getParameter());
 		
 		RatioNonBayesianDeGroot mixedNodes = new RatioNonBayesianDeGroot(ratio, possibleDistributions, new GaussianFactory());
@@ -142,7 +142,7 @@ public class RatioNonBayesianDeGroot {
             Graph<Node, Edge> graph = null;
             System.out.println("Ratio\tConvergence/"
                     + numTrialsPerRatio + "\tMeanStepsToConvergence\tStdDevStepsToConvergence");
-                for(double ratio = 1.0; ratio >= 0.5; ratio -= 0.05) {
+                for(double ratio = 1.0; ratio >= 0.0; ratio -= 0.05) {
                     List<Integer> stepsToConvergence = new ArrayList<>();
                     for(int i = 0; i < numTrialsPerRatio; i++) {
                             graph = runNGaussiansHard(20, ratio);

### 2012-12-11 src/eecs598/experiments/RatioNonBayesianDeGroot.java
Fixes to distance metric and adding DeGroot node convergence to ConvergenceInspector

@@ -53,11 +53,12 @@ public class RatioNonBayesianDeGroot {
 	}
 
 	public Graph<Node, Edge> runExperiment(ExperimentController controller, int numVertices, double p) {
-		ErdosRenyiGenerator<Node, Edge> erdosRenyiGenerator = new ErdosRenyiGenerator<Node, Edge>(
-				graphFactory, nodeFactory, edgeFactory, numVertices, p);
+            //		ErdosRenyiGenerator<Node, Edge> erdosRenyiGenerator = new ErdosRenyiGenerator<Node, Edge>(
+            //				graphFactory, nodeFactory, edgeFactory, numVertices, p);
 		
                 //		Graph<Node, Edge> graph = erdosRenyiGenerator.create();
-                Graph<Node, Edge> graph = new GeneratorFactories.ErdosRenyiFactory(15, 1.0).create(nodeFactory, edgeFactory, graphFactory).create();
+                //Graph<Node, Edge> graph = new GeneratorFactories.ErdosRenyiFactory(15, 1.0).create(nodeFactory, edgeFactory, graphFactory).create();
+            Graph<Node, Edge> graph = new GeneratorFactories.KleinbergGenerator(5, 2).create(nodeFactory, edgeFactory, graphFactory).create();
                 GraphConnector connector = new GraphConnector();
                 connector.makeConnected(graph, edgeFactory);
 		
@@ -68,12 +69,12 @@ public class RatioNonBayesianDeGroot {
 		ConvergenceInspector convergenceInspector = new ConvergenceInspector();
 		boolean converged = convergenceInspector.haveConverged(graph.getVertices());
 //		System.out.println("\tConvergence: " + converged);
-/*		if(converged) {
+		if(converged) {
                     //System.out.println("\tParameter: " + convergenceInspector.getConvergedParameter(graph.getVertices()));
                     System.out.println("Converged in " + stepsToConvergence + " steps");
 		} else {
                     System.out.println("Did not converge");
-                    }*/
+                    }
 		return graph;
 	}
 	

### 2012-12-11 src/eecs598/experiments/RatioNonBayesianDeGroot.java
Added other graph types to RatioNonBayesianDeGroot

@@ -15,6 +15,7 @@ import eecs598.Edge;
 import eecs598.ManyRandomDrawsBeliefEstimator;
 import eecs598.DistanceBeliefEstimator;
 import eecs598.Node;
+import eecs598.NonBayesianNode;
 import eecs598.NopParameterEstimator;
 import eecs598.RandomDrawBeliefEstimator;
 import eecs598.experiments.analyzer.AverageBeliefTracker;
@@ -53,15 +54,32 @@ public class RatioNonBayesianDeGroot {
 	}
 
 	public Graph<Node, Edge> runExperiment(ExperimentController controller, int numVertices, double p) {
+            NonBayesianNode.listensToSignalRatio = 0.5;
+
             //		ErdosRenyiGenerator<Node, Edge> erdosRenyiGenerator = new ErdosRenyiGenerator<Node, Edge>(
             //				graphFactory, nodeFactory, edgeFactory, numVertices, p);
-		
                 //		Graph<Node, Edge> graph = erdosRenyiGenerator.create();
-                //Graph<Node, Edge> graph = new GeneratorFactories.ErdosRenyiFactory(15, 1.0).create(nodeFactory, edgeFactory, graphFactory).create();
-            Graph<Node, Edge> graph = new GeneratorFactories.KleinbergGenerator(5, 2).create(nodeFactory, edgeFactory, graphFactory).create();
-                GraphConnector connector = new GraphConnector();
-                connector.makeConnected(graph, edgeFactory);
-		
+
+                /*Graph<Node, Edge> graph = new GeneratorFactories.ErdosRenyiFactory(15, 1.0)
+                        .create(nodeFactory, edgeFactory, graphFactory).create();
+            Graph<Node, Edge> graph = new GeneratorFactories.KleinbergGenerator(5, 2)
+                    .create(nodeFactory, edgeFactory, graphFactory).create();
+
+            int initialNodeCount = 10;
+            int edgesPerTimestep = 5;
+            int generationTimesteps = 10;
+            Graph<Node, Edge> graph = new GeneratorFactories.BarabasiAlbertFactory(initialNodeCount, edgesPerTimestep, generationTimesteps)
+            .create(nodeFactory, edgeFactory, graphFactory).create();*/
+
+            int nodeCount = 30;
+            int edgeToNodeRatio = 3;
+            int generationTimesteps = 50;
[…]

### 2012-12-11 src/eecs598/experiments/RatioNonBayesianDeGroot.java
Data for tests of ratio of Non-Bayesian to DeGroot nodes versus time to convergence for several graph types.

@@ -60,22 +60,22 @@ public class RatioNonBayesianDeGroot {
             //				graphFactory, nodeFactory, edgeFactory, numVertices, p);
                 //		Graph<Node, Edge> graph = erdosRenyiGenerator.create();
 
-                /*Graph<Node, Edge> graph = new GeneratorFactories.ErdosRenyiFactory(15, 1.0)
-                        .create(nodeFactory, edgeFactory, graphFactory).create();
-            Graph<Node, Edge> graph = new GeneratorFactories.KleinbergGenerator(5, 2)
-                    .create(nodeFactory, edgeFactory, graphFactory).create();
+                Graph<Node, Edge> graph = new GeneratorFactories.ErdosRenyiFactory(15, 1.0)
+                  .create(nodeFactory, edgeFactory, graphFactory).create();
+            /*            Graph<Node, Edge> graph = new GeneratorFactories.KleinbergGenerator(5, 2)
+                          .create(nodeFactory, edgeFactory, graphFactory).create();*/
 
-            int initialNodeCount = 10;
+            /*            int initialNodeCount = 10;
             int edgesPerTimestep = 5;
             int generationTimesteps = 10;
             Graph<Node, Edge> graph = new GeneratorFactories.BarabasiAlbertFactory(initialNodeCount, edgesPerTimestep, generationTimesteps)
             .create(nodeFactory, edgeFactory, graphFactory).create();*/
 
-            int nodeCount = 30;
+            /*            int nodeCount = 30;
             int edgeToNodeRatio = 3;
             int generationTimesteps = 50;
             Graph<Node, Edge> graph = new GeneratorFactories.EppsteinFactory(nodeCount, edgeToNodeRatio * nodeCount, generationTimesteps)
-                    .create(nodeFactory, edgeFactory, graphFactory).create();
+            .create(nodeFactory, edgeFactory, graphFactory).create();*/
 
             GraphConnector connector = new GraphConnector();
             connector.makeConnected(graph, edgeFactory);
@@ -87,12 +87,12 @@ public class RatioNonBayesianDeGroot {
 		ConvergenceInspector convergenceInspector = new ConvergenceInspector();
 		boolean converged = convergenceInspector.haveConverged(graph.getVertices());
 //		System.out.println("\tConvergence: " + converged);
-		if(converged) {
+/*		if(converged) {
[…]

### 2012-12-11 docs/paper.tex
Added figure for trapezoidal distribution
Fixed image to work for both latex and pdflatex
Added some discussion of simulation and conclusion to paper.

@@
 \usepackage{amsfonts} % For bold number set font
+\usepackage{graphicx}
+\usepackage[font=bf]{caption}
 \begin{document}
@@
 The model allows for a variety of generative methods to be used for creation of the network structure such as Erdos-Renyi, Watts-Strogatz, Kleinberg's Small-World Model, or a power law distribution.
-We investigate each of these network types in section \{ \}.% @todo[DDC] Refer to simulation results
+We investigate several of these network types in simulation, described in section~\ref{sec:simulation}.
 
@@
 
-% @todo[DDC] Graph/figure of this would probably be good to have.
-
 The slope $\{ m^* \in \mathbb{R} : m_{min} = -2 \le m^* \le 2 = m_{max} \}$ will be the defining characteristic of the distribution.
 We have chosen to bound $m^*$ between -2 and 2 and add the term $\frac{1}{2}(2-m^*)$ so that the support of $p^*(x)$  is always over $[0,1]$.
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.8]{trapezoidalDistribution}
+\caption{Trapezoidal Probability Distribution}
+\end{figure}
 
@@
 
-The second method we consider for creating a probability distribution over the set of belief states $\Theta$ is to define an exponential distance metric such that
+The second method we consider for creating a probability distribution over the set of belief states $\Theta$ is to define a distance metric such that
 
 \begin{equation}
-\mu_{j,t}^\prime(\theta_k) \propto e^{-(m_{j,t}-\hat{m_k})^2}
+\mu_{j,t}^\prime(\theta_k) \propto \frac{1}{(m_{j,t}-\hat{m_k})^2}
 \end{equation}
@@
 \begin{equation}
-q_{j,t} = \sum_{k=1}^n e^{-(m_{j,t}-\hat{m_k})^2}
+q_{j,t} = \sum_{k=1}^n \frac{1}{(m_{j,t}-\hat{m_k})^2}
 \end{equation}
@@
 \begin{equation}
-\mu_{j,t}^\prime(\theta_k) = e^{-(m_{j,t}-\hat{m_i})^2} / q_{j,t}
+\mu_{j,t}^\prime(\theta_k) = \frac{(m_{j,t}-\hat{m_i})^{-2}}{q_{j,t}}
 \end{equation}
@@
 
+\section{Simulation}
+
+In order to seek insight about the behavior of our model we performed a series of simulations using the JUNG network/graph software library \cite{website:JUNGGraphLibrary}.
+For each simulation, $\Theta$ consisted of two Gaussian distributions with means of 100 and 105 and standard deviation of 1.
+Each trial was run until all nodes have converged upon the true state or some maximum number of timesteps had elapsed.
+
+\subsection{Node Ratio vs. Convergence Time}
+\label{sec:simulation}
+
+In order to characterize the effect of naive DeGroot nodes on Non-Bayesian social learning we simulated time taken for convergence versus the ratio of Non-Bayesian to DeGroot nodes in a network.
+To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian received any signals; the other 50\% needed to rely completely on learning from their neighbors.
+Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.
+
+% Graph here
+
+The data show a somewhat counterintuitive result: the presence of naive DeGroot nodes actually tends to accelerate the speed of convergence.
+Further investigation showed this to be a result of the process used to convert DeGroot belief to Non-Bayesian belief.
+The conversion method of section~\ref{sec:likelihood_metric} tends to result in a belief distribution that is heavily skewed to a single $\theta_i$.
+This relative ``certainty'' of the DeGroot nodes is picked up by their Non-Bayesian neighbors, bringing them more quickly to convergence.
+
+% Graph here
+
+Thus we see that the presence of naive, non-observant agents in a graph can actually accelerate the rate of learning due to eagerness of these nodes to settle on a single set of beliefs.
+
+\subsection{Graph Size vs. Convergence Time}
+
+We also evaluated time to convergence versus graph size for several network types.
+These simulations were performed with a ratio of 0.8 Non-Bayesian to DeGroot nodes, where 60\% of Non-Bayesian nodes received signals from the true probability distribution and 40\% had to rely completely on information from neighbors.
+
+% Graph here
+
+Time required for convergence appears to be linear with respect to the number of nodes in the graph.
+
 \section{Conclusion}
 
-% Can discuss in conclusion that future work could either focus on figuring out how to do this or on developing other ways of doing the DeGroot-to-Non-Bayesian conversion that make such proofs easier.
+We have developed a model that allows the Non-Bayesian social learning method of Jadbabaie et.
+al.
+to take place in a graph that also contains nodes performing simple DeGroot-style belief updates.
+This model can be used as a theoretical framework for evaluating the effect that naive, non-observant agents can have on a network of more sophisticated learners.
+
+We performed a series of simulations to obtain greater intuition about our model.
+Some results were counterintuitive, such as the fact that DeGroot nodes can actually accelerate convergence due to a tendency towards certainty in their beliefs.
+
+Future work could focus on proving further theoretical results for our model, such as specific conditions necessary to guarantee convergence.
+This may involve development of different methods for converting DeGroot to Non-Bayesian belief that allow for easier theoretical analysis.
+Future work could also investigate the effects of different choices for this method on convergence time.
 

### 2012-12-11 docs/paper.tex
Initial add of simulation graphs to paper
Two column format, changes to the way images are displayed.
Added some captions and citations

@@
-\documentclass[a4paper,12pt]{article}
+%\documentclass[a4paper,12pt]{article}
+\documentclass[letterpaper, 10pt, conference]{ieeeconf}
 \usepackage{amsmath} % For 'cases' curly brace
@@
 \begin{document}
-\title{Mixed Non-Bayesian and DeGroot Learning}
+\title{\LARGE \bf
+Mixed Non-Bayesian and DeGroot Learning
+}
 \author{Pedro d'Aquino\\pdaquino@umich.edu \and Dan Clark\\ddclark@umich.edu}
@@
 \centering
-\includegraphics[scale=0.8]{trapezoidalDistribution}
+%\includegraphics[scale=0.8]{trapezoidalDistribution}
+\includegraphics[width=0.48\textwidth]{trapezoidalDistribution}
 \caption{Trapezoidal Probability Distribution}
+\label{fig:trapezoidal}
 \end{figure}
@@
 
-% @todo[DDC] More detail for derivation/explanation of likelihood?
 The likelihood function $\ell_i(s_i|\theta_k)$ can be obtained from the probability distribution function represented by the belief state $\theta_k$.
@@
 \section{Simulation}
+\label{sec:simulation}
 
@@
 \subsection{Node Ratio vs. Convergence Time}
-\label{sec:simulation}
+\label{sec:node_ratio_vs_convergence_time}
 
 In order to characterize the effect of naive DeGroot nodes on Non-Bayesian social learning we simulated time taken for convergence versus the ratio of Non-Bayesian to DeGroot nodes in a network.
+This simulation was performed for a several graph types: Barabasi-Albert preferential attachment~\cite{Barabasi}, Kleinberg small-world~\cite{KleinbergSmallWorld}, Eppstein power law~\cite{Eppstein}, and the complete graph.
 To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian received any signals; the other 50\% needed to rely completely on learning from their neighbors.
@@
 
-% Graph here
+\begin{figure*}[t]
+%\hspace*{0.1in}
+%\centerline{\includegraphics[scale=0.8]{figures/nb_ratio}}
+\centering
+\includegraphics[width=0.9\textwidth]{figures/nb_ratio}
+\caption{Time to convergence decreases as the ratio of Non-Bayesian to DeGroot nodes decreases}
+\label{fig:nb_ratio}
+\end{figure*}
 
-The data show a somewhat counterintuitive result: the presence of naive DeGroot nodes actually tends to accelerate the speed of convergence.
+The results, shown in figure~\ref{fig:nb_ratio}, are somewhat counterintuitive: the presence of naive DeGroot nodes actually tends to accelerate the speed of convergence.
 Further investigation showed this to be a result of the process used to convert DeGroot belief to Non-Bayesian belief.
@@
 
-% Graph here
+We can see this process in more detail in figure~\ref{fig:dg_faster}.
+
+\begin{figure}[th]
+%\hspace*{0.1in}
+%\centerline{\includegraphics[scale=0.8]{figures/dg_faster}}
+\centering
+\includegraphics[width=0.48\textwidth]{figures/dg_faster}
+\caption{@todo[DDC]}
+\label{fig:dg_faster}
+\end{figure}
 
@@
 
-We also evaluated time to convergence versus graph size for several network types.
+We also evaluated time to convergence versus graph size for each of the network types tested in section~\ref{sec:node_ratio_vs_convergence_time}.
 These simulations were performed with a ratio of 0.8 Non-Bayesian to DeGroot nodes, where 60\% of Non-Bayesian nodes received signals from the true probability distribution and 40\% had to rely completely on information from neighbors.
 
-% Graph here
+\begin{figure*}[h]
+%\hspace*{0.1in}
+%\centerline{\includegraphics[scale=0.8]{figures/convergence_time}}
+\centering
+\includegraphics[width=.9\textwidth]{figures/convergence_time}
+\caption{Time to convergence increases linearly with the size of the graph}
+\label{fig:convergence_time}
+\end{figure*}
 
-Time required for convergence appears to be linear with respect to the number of nodes in the graph.
+The results, shown in figure~\ref{fig:convergence_time}, show that time required for convergence appears to be linear with respect to the number of nodes in the graph.
 

### 2012-12-11 docs/paper.tex
Description of why random draw method fails

@@
 
+\subsection{Random Draw Belief Conversion Method}
+
+An important discovery from simulation was that the random draw method of conversion from DeGroot to Non-Bayesian belief described in section~\ref{sec:draw_from_degroot} can lead to unrealistically skewed belief distributions.
+This primarily occurred in cases using Gaussian distributions where the means of the possible distributions represented by each belief state $\theta_i \in \Theta$ are relatively far apart.
+For example, suppose that $n = 2$, $\theta_0 \sim N(100, 1)$ and $\theta_1 \sim N(105, 1)$.
+A DeGroot node $d$ will have an initial belief of 102.5, and will therefore create a Bayesian belief distribution by drawing from the distribution $N(102.5, 1)$.
+There is now a significant (0.318) probability that it will draw a point at least one standard deviation outside of the mean, e.g.
+$s_{d,t}^\prime = 101.5$.
+But the value 101.5 is significantly more likely to have been drawn from the probability distribution $N(100, 1)$ versus the distribution $N(105, 1)$.
+Therefore $d$ will report that it is almost certain that the true state is $\theta_0 \sim N(100, 1)$ when in reality it should have a relatively evenly spread belief distribution.
+
+After the discovery of this difficulty, we evaluated the distance metric described in section~\ref{sec:likelihood_metric} and found it to give much more desirable results.
+Therefore that method was used throughout all simulations described in the remainder of this section.
+
 \subsection{Node Ratio vs. Convergence Time}
@@
 This simulation was performed for a several graph types: Barabasi-Albert preferential attachment~\cite{Barabasi}, Kleinberg small-world~\cite{KleinbergSmallWorld}, Eppstein power law~\cite{Eppstein}, and the complete graph.
-To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian received any signals; the other 50\% needed to rely completely on learning from their neighbors.
+To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian nodes received any signals; the other 50\% needed to rely completely on learning from their neighbors.
 Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.
 
-\begin{figure*}[t]
+\begin{figure*}[h]
 %\hspace*{0.1in}

### 2012-12-11 docs/paper.tex
Added two paragraphs on DG nodes helping convergence times.

--- 2012-12-11 docs/paper.tex
@@
 %\documentclass[a4paper,12pt]{article}
-\documentclass[letterpaper, 10pt, conference]{ieeeconf}
+\documentclass[letterpaper, 11pt, conference]{ieeeconf}
 \usepackage{amsmath} % For 'cases' curly brace
@@
 
-In order to characterize the effect of naive DeGroot nodes on Non-Bayesian social learning we simulated time taken for convergence versus the ratio of Non-Bayesian to DeGroot nodes in a network.
+In order to characterize the effect of naive DeGroot nodes on Non-Bayesian social learning we simulated the time taken for convergence versus the ratio of Non-Bayesian to DeGroot nodes in a network.
 This simulation was performed for a several graph types: Barabasi-Albert preferential attachment~\cite{Barabasi}, Kleinberg small-world~\cite{KleinbergSmallWorld}, Eppstein power law~\cite{Eppstein}, and the complete graph.
@@
 
-The results, shown in figure~\ref{fig:nb_ratio}, are somewhat counterintuitive: the presence of naive DeGroot nodes actually tends to accelerate the speed of convergence.
-Further investigation showed this to be a result of the process used to convert DeGroot belief to Non-Bayesian belief.
+The results, shown in Figure~\ref{fig:nb_ratio}, are somewhat counterintuitive: the presence of naive DeGroot nodes actually tends to accelerate the speed of convergence.
+Further investigation showed this to be a result of the process used to convert DeGroot beliefs to Non-Bayesian belief.
 The conversion method of section~\ref{sec:likelihood_metric} tends to result in a belief distribution that is heavily skewed to a single $\theta_i$.
@@
 
-We can see this process in more detail in figure~\ref{fig:dg_faster}.
+We can see this process in more detail in Figure~\ref{fig:dg_faster}, which shows the average beliefs in $\Theta^*$ for the intial steps of two trials on a complete graph.
+It is clear that the DeGroot nodes essentially act as amplifiers, magnifying the initial belief updates of the Non-Bayesian nodes.
+This will in turn strengthen the Non-Bayesian's nodes beliefs in $\Theta*$ (through Equation \ref{eq:non_bayesian_update}), which are then incorporated into the DeGroot nodes' parameter estimates.
+This feedback cycle increases the speed of convergence.
+
+In essence, this happens because belief estimation algorithm of the DeGroot nodes is inherently aggressive.
+It is interesting to note that this can have negative effects on convergence when there is significant noise in the signal received by the Non-Bayesian nodes.
+If a Non-Bayesian node receives an ``unlucky'' draw that skews its belief distribution away from $\Theta*$, this error will be amplified by the DeGroot nodes.
+Since there was no noise in our simulations, the presence of DeGroot nodes is beneficial.
+We find it interesting that the presence of naive, non-observant agents in a graph can actually accelerate the rate of learning due to eagerness of these nodes to settle on a single set of beliefs.
 
@@
 \includegraphics[width=0.48\textwidth]{figures/dg_faster}
-\caption{@todo[DDC]}
+\caption{The average beliefs in $\Theta^*$, the true distribution, for the two types of nodes during simulations with 0\% and 20\% of DeGroot nodes in a complete graph.
+The possible distributions were Gaussians centered at 100 and 105 with $\sigma=1$.
+All random seeds were fixed such that in both runs the Non-Bayesian nodes received the exact same sequence of draws.
+DeGroot nodes' beliefs were estimated using the distance metric.
+The figure shows how DeGroot nodes help amplify the initial belief updates of Non-Bayesian nodes, which leads to overall faster convergence.}
 \label{fig:dg_faster}
 \end{figure}
-
-Thus we see that the presence of naive, non-observant agents in a graph can actually accelerate the rate of learning due to eagerness of these nodes to settle on a single set of beliefs.
 

### 2012-12-11 src/eecs598/experiments/ConvergenceStressTest.java

@@ -4,6 +4,7 @@ import java.io.FileNotFoundException;
 import java.io.FileOutputStream;
 import java.io.IOException;
 import java.io.ObjectOutputStream;
+import java.io.PrintStream;
 import java.util.Date;
 
 import org.apache.commons.collections15.Factory;
@@ -11,11 +12,14 @@ import org.apache.commons.collections15.Factory;
 import edu.uci.ics.jung.algorithms.generators.GraphGenerator;
 import edu.uci.ics.jung.graph.Graph;
 import edu.uci.ics.jung.graph.UndirectedGraph;
+import eecs598.DistanceBeliefEstimator;
 import eecs598.Edge;
 import eecs598.ManyRandomDrawsBeliefEstimator;
 import eecs598.Node;
 import eecs598.NonBayesianNode;
 import eecs598.NopParameterEstimator;
+import eecs598.experiments.analyzer.AverageBeliefTracker;
+import eecs598.experiments.analyzer.NodeType;
 import eecs598.experiments.visualization.NetworkVisualizer;
 import eecs598.factories.EdgeFactory;
 import eecs598.factories.GraphFactory;
@@ -68,11 +72,15 @@ public class ConvergenceStressTest {
 			experiment.setConvergenceTestStep(convergenceTestGranularity);
 			experiment.setMaxConvergenceTimesteps(maxTimesteps);
 			
+			experiment.attachAnalyzer(new AverageBeliefTracker(new PrintStream("nonBayesianBeliefs.txt"), NodeType.NonBayesian));
+			experiment.attachAnalyzer(new AverageBeliefTracker(new PrintStream("deGrootBeliefs.txt"), NodeType.DeGroot));
+			
 			Factory<Node> nodeFactory = new RatioNodeFactory(
 					ratioNonBayesian,
 					setup.getPossibleDistributions(),
 					new NopParameterEstimator(),
-					new ManyRandomDrawsBeliefEstimator(setup.getDistributionFactory()));
+					//new ManyRandomDrawsBeliefEstimator(setup.getDistributionFactory()));
+					new DistanceBeliefEstimator());
 			
 			Factory<Edge> edgeFactory = new EdgeFactory();
 			
@@ -115,9 +123,10 @@ public class ConvergenceStressTest {
 	
 	public static void main(String[] args) throws IOException {
 		ConvergenceStressTest stressTest = new ConvergenceStressTest();
[…]

### 2012-12-11 src/eecs598/experiments/ConvergenceTimeTest.java

@@ -72,7 +72,7 @@ public class ConvergenceTimeTest {
 	 */
 	public MeanAndStdDev run(int nRuns, Factory<ExperimentalSetup> setupFactory) throws IOException {
 		
-		NonBayesianNode.listensToSignalRatio = 0.4;
+		NonBayesianNode.listensToSignalRatio = 0.6;
 		
 		List<Double> convergenceTimes = new ArrayList<Double>();
 		ExperimentalSetup setup = setupFactory.create();
@@ -91,10 +91,10 @@ public class ConvergenceTimeTest {
 		
 		Factory<UndirectedGraph<Node, Edge>> graphFactory = new GraphFactory();
 		
-		GraphGenerator<Node, Edge> generator = generatorFactory.create(nodeFactory, edgeFactory, graphFactory);
 		GraphConnector connector = new GraphConnector();
 		
 		for(int i = 0; i < nRuns; i++) {
+			GraphGenerator<Node, Edge> generator = generatorFactory.create(nodeFactory, edgeFactory, graphFactory);
 			Graph<Node, Edge> graph = generator.create();
 			connector.makeConnected(graph, edgeFactory);
 			if(!connector.isConnected(graph)) throw new RuntimeException("Graph is not connected!");
@@ -103,13 +103,13 @@ public class ConvergenceTimeTest {
 				//System.out.println(timesteps);
 				convergenceTimes.add((double)timesteps);
 			} catch(MaxTimestepsExceededException e) {
-				//experiment.run(graph, 1);
-				try {
-					experiment.runUntilConvergence(graph);
-				} catch (MaxTimestepsExceededException e1) {
-					// TODO Auto-generated catch block
-					e1.printStackTrace();
-				}
+//				//experiment.run(graph, 1);
+//				try {
+//					experiment.runUntilConvergence(graph);
+//				} catch (MaxTimestepsExceededException e1) {
+//					// TODO Auto-generated catch block
+//					e1.printStackTrace();
+//				}
 				String filename =  "no_convergence_" + new Date().getTime() + ".jung";
 				saveGraph(graph, filename); 
 				System.out.println("\tNo convergence: saved to " + filename);
@@ -131,8 +131,8 @@ public class ConvergenceTimeTest {
 	
 	public static void main(String[] args) throws IOException {
 		//String arg = args[0];
[…]

### 2012-12-11 src/eecs598/experiments/DistributionRepository.java

@@ -98,6 +98,7 @@ public class DistributionRepository {
 			possibleDistributions.add(new Gaussian(startingMean + i*step));
 		}
 		
-		return chooseRandom(possibleDistributions);
+		//return chooseRandom(possibleDistributions);
+		return possibleDistributions.get(0);
 	}
 }

### 2012-12-11 src/eecs598/experiments/Experiment.java

@@ -7,6 +7,7 @@ import edu.uci.ics.jung.graph.Graph;
 import edu.uci.ics.jung.graph.UndirectedGraph;
 import eecs598.Edge;
 import eecs598.Node;
+import eecs598.experiments.analyzer.ExperimentAnalyzer;
 
 /**
  * 
@@ -40,6 +41,10 @@ public class Experiment {
 	public Graph<Node, Edge> run(Graph<Node, Edge> graph, int numTimesteps) {
 		getExperimentController().run(graph, numTimesteps);
 		return graph;
+	}
+	
+	public void attachAnalyzer(ExperimentAnalyzer analyzer) {
+		getExperimentController().attachAnalyzer(analyzer);
 	}
 
 	/**

### 2012-12-11 src/eecs598/experiments/LoadGraph.java

@@ -15,14 +15,14 @@ public class LoadGraph {
 	public static void main(String args[]) throws ClassNotFoundException, IOException {
 	    NonBayesianNode.listensToSignalRatio = 0.9;
 	    
-		FileInputStream underlyingStream2 = new FileInputStream( "no_convergence_1355182809308.jung" ); 
+		FileInputStream underlyingStream2 = new FileInputStream( "no_convergence_1355184387859.jung" ); 
 		//FileInputStream underlyingStream2 = new FileInputStream( "no_conv_2.jung" );
 	    ObjectInputStream deserializer = new ObjectInputStream( underlyingStream2 );
 	    UndirectedSparseGraph<Node, Edge> loadedGraph = (UndirectedSparseGraph<Node, Edge>) deserializer.readObject(); //EXCEPTION THROWN HERE
 	    deserializer.close();
 	    underlyingStream2.close();
 	    
-	    //resetGraph(loadedGraph);
+	    
 	    
 	    NetworkVisualizer visualizer = new NetworkVisualizer();
 	    visualizer.showGraph(loadedGraph);
@@ -30,10 +30,13 @@ public class LoadGraph {
 	    ConvergenceInspector inspector = new ConvergenceInspector();
 	    System.out.println("Convergence before: " + inspector.haveConverged(loadedGraph.getVertices()));
 	    
-	    ExperimentController controller = new ExperimentController(new Gaussian(105.0));
-	    //controller.run(loadedGraph, 400);
+	    ExperimentController controller = new ExperimentController(new Gaussian(130.0));
+	    System.in.read();
+	    resetGraph(loadedGraph);
+	    controller.run(loadedGraph, 400);
+	    System.in.read();
 	    visualizer.refresh();
-	    //controller.run(loadedGraph, 3000);
+	    controller.run(loadedGraph, 3000);
 	    
 	    System.out.println("Convergence after: " + inspector.haveConverged(loadedGraph.getVertices()));
 	    //visualizer.showGraph(loadedGraph);

### 2012-12-11 src/eecs598/probability/Gaussian.java

@@ -3,6 +3,7 @@ package eecs598.probability;
 import java.io.Serializable;
 
 import cern.jet.random.Normal;
+import cern.jet.random.engine.MersenneTwister;
 import cern.jet.random.engine.RandomEngine;
 
 public class Gaussian implements Distribution, Serializable {
@@ -14,7 +15,8 @@ public class Gaussian implements Distribution, Serializable {
 	
 	public Gaussian(double mean) {
 		this.mean = mean;
-		this.normal = new Normal(mean, stdDev, RandomEngine.makeDefault());
+		//this.normal = new Normal(mean, stdDev, RandomEngine.makeDefault());
+		this.normal = new Normal(mean, stdDev, new MersenneTwister());
 	}
 	
 	@Override

### 2012-12-11 docs/paper.tex

@@
 
-In order to characterize the effect of naive DeGroot nodes on Non-Bayesian social learning we simulated the time taken for convergence versus the ratio of Non-Bayesian to DeGroot nodes in a network.
+In order to characterize the effect of naive DeGroot nodes on Non-Bayesian social learning we simulated time taken for convergence versus the ratio of Non-Bayesian to DeGroot nodes in a network.
 This simulation was performed for a several graph types: Barabasi-Albert preferential attachment~\cite{Barabasi}, Kleinberg small-world~\cite{KleinbergSmallWorld}, Eppstein power law~\cite{Eppstein}, and the complete graph.
-To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian received any signals; the other 50\% needed to rely completely on learning from their neighbors.
+To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian nodes received any signals; the other 50\% needed to rely completely on learning from their neighbors.
 Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.
 
-\begin{figure*}[t]
+\begin{figure*}[h]
 %\hspace*{0.1in}

### 2012-12-11 docs/paper.tex
Longer captions.

@@
 This simulation was performed for a several graph types: Barabasi-Albert preferential attachment~\cite{Barabasi}, Kleinberg small-world~\cite{KleinbergSmallWorld}, Eppstein power law~\cite{Eppstein}, and the complete graph.
-To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian nodes received any signals; the other 50\% needed to rely completely on learning from their neighbors.
-Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.
 
-\begin{figure*}[h]
+\begin{figure*}[t]
 %\hspace*{0.1in}
@@
 \includegraphics[width=0.9\textwidth]{figures/nb_ratio}
-\caption{Time to convergence decreases as the ratio of Non-Bayesian to DeGroot nodes decreases}
+\caption{Time to convergence as the ratio of Non-Bayesian to DeGroot nodes decreases.
+For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=5$.
+To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian nodes received any signals; the other 50\% needed to rely completely on learning from their neighbors.
+Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.
+Unexpectedly, the time to convergence is inversely proportional to the ratio of Non-Bayesian nodes.}
 \label{fig:nb_ratio}
@@
 
-\begin{figure}[th]
+\begin{figure}[t]
 %\hspace*{0.1in}
@@
 \includegraphics[width=.9\textwidth]{figures/convergence_time}
-\caption{Time to convergence increases linearly with the size of the graph}
+\caption{Time to convergence as the size of the graph grows.
+Each datapoint is the average of 200 trials.
+For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=5$.
+DeGroot nodes were on average 20\% of the total vertices.
+Only 60\% of the Non-Bayesian nodes were receiving signals.
+We also show $R^2$ values for a linear regression for the different types of graph.
+We can see that the convergence time increases linearly with the size of the graph, and that the complete graph takes substantially longer to converge.
+}
 \label{fig:convergence_time}

### 2012-12-12 docs/paper.tex
Figures with larger font size and at the top of each page.
Small change to Introduction
Small typos.

@@
 
+\begin{figure*}[t]
+%\hspace*{0.1in}
+%\centerline{\includegraphics[scale=0.8]{figures/nb_ratio}}
+\centering
+\includegraphics[width=0.9\textwidth]{figures/nb_ratio}
+\caption{Time to convergence as the ratio of Non-Bayesian to DeGroot nodes decreases.
+For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=5$.
+To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian nodes received any signals; the other 50\% needed to rely completely on learning from their neighbors.
+Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.
+Unexpectedly, the time to convergence is inversely proportional to the ratio of Non-Bayesian nodes.}
+\label{fig:nb_ratio}
+\end{figure*}
+
 \section{Convergence}
@@
 That is, $\mu_{b,t}(\theta^*) \to 1$ as $t \to \infty$ where $\theta^*$ is the correct belief state.
+
+\begin{figure*}[t]
+%\hspace*{0.1in}
+%\centerline{\includegraphics[scale=0.8]{figures/dg_faster}}
+\centering
+\includegraphics[width=0.9\textwidth]{figures/dg_faster}
+\caption{The average beliefs in $\Theta^*$, the true distribution, for the two types of nodes during simulations with 0\% and 20\% of DeGroot nodes in a complete graph.
+The possible distributions were Gaussians centered at 100 and 105 with $\sigma=1$.
+All random seeds were fixed such that in both runs the Non-Bayesian nodes received the exact same sequence of draws.
+DeGroot nodes' beliefs were estimated using the distance metric.
+The figure shows how DeGroot nodes help amplify the initial belief updates of Non-Bayesian nodes, which leads to overall faster convergence.}
+\label{fig:dg_faster}
+\end{figure*}
 
@@
 
+\begin{figure*}[t]
+%\hspace*{0.1in}
+%\centerline{\includegraphics[scale=0.8]{figures/convergence_time}}
+\centering
+\includegraphics[width=.9\textwidth]{figures/convergence_time}
+\caption{Time to convergence as the size of the graph grows.
+Each datapoint is the average of 200 trials.
+For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=5$.
+DeGroot nodes were on average 20\% of the total vertices.
+Only 60\% of the Non-Bayesian nodes were receiving signals.
+We also show $R^2$ values for a linear regression for the different types of graph.
+We can see that the convergence time increases linearly with the size of the graph, and that the complete graph takes substantially longer to converge.
+}
+\label{fig:convergence_time}
+\end{figure*}
+
 In order to seek insight about the behavior of our model we performed a series of simulations using the JUNG network/graph software library \cite{website:JUNGGraphLibrary}.
@@
 
-\begin{figure*}[t]
-%\hspace*{0.1in}
-%\centerline{\includegraphics[scale=0.8]{figures/nb_ratio}}
-\centering
-\includegraphics[width=0.9\textwidth]{figures/nb_ratio}
-\caption{Time to convergence as the ratio of Non-Bayesian to DeGroot nodes decreases.
-For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=5$.
-To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian nodes received any signals; the other 50\% needed to rely completely on learning from their neighbors.
-Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.
-Unexpectedly, the time to convergence is inversely proportional to the ratio of Non-Bayesian nodes.}
-\label{fig:nb_ratio}
-\end{figure*}
-
 The results, shown in Figure~\ref{fig:nb_ratio}, are somewhat counterintuitive: the presence of naive DeGroot nodes actually tends to accelerate the speed of convergence.
@@
 It is clear that the DeGroot nodes essentially act as amplifiers, magnifying the initial belief updates of the Non-Bayesian nodes.
-This will in turn strengthen the Non-Bayesian's nodes beliefs in $\Theta*$ (through Equation \ref{eq:non_bayesian_update}), which are then incorporated into the DeGroot nodes' parameter estimates.
+This will in turn strengthen the Non-Bayesian's nodes beliefs in $\Theta^*$ (through Equation \ref{eq:non_bayesian_update}), which are then incorporated into the DeGroot nodes' parameter estimates.
 This feedback cycle increases the speed of convergence.
@@
 It is interesting to note that this can have negative effects on convergence when there is significant noise in the signal received by the Non-Bayesian nodes.
-If a Non-Bayesian node receives an ``unlucky'' draw that skews its belief distribution away from $\Theta*$, this error will be amplified by the DeGroot nodes.
+If a Non-Bayesian node receives an ``unlucky'' draw that skews its belief distribution away from $\Theta^*$, this error will be amplified by the DeGroot nodes.
 Since there was no noise in our simulations, the presence of DeGroot nodes is beneficial.
 We find it interesting that the presence of naive, non-observant agents in a graph can actually accelerate the rate of learning due to eagerness of these nodes to settle on a single set of beliefs.
-
-\begin{figure}[t]
-%\hspace*{0.1in}
-%\centerline{\includegraphics[scale=0.8]{figures/dg_faster}}
-\centering
-\includegraphics[width=0.48\textwidth]{figures/dg_faster}
-\caption{The average beliefs in $\Theta^*$, the true distribution, for the two types of nodes during simulations with 0\% and 20\% of DeGroot nodes in a complete graph.
-The possible distributions were Gaussians centered at 100 and 105 with $\sigma=1$.
-All random seeds were fixed such that in both runs the Non-Bayesian nodes received the exact same sequence of draws.
-DeGroot nodes' beliefs were estimated using the distance metric.
-The figure shows how DeGroot nodes help amplify the initial belief updates of Non-Bayesian nodes, which leads to overall faster convergence.}
-\label{fig:dg_faster}
-\end{figure}
 
@@
 These simulations were performed with a ratio of 0.8 Non-Bayesian to DeGroot nodes, where 60\% of Non-Bayesian nodes received signals from the true probability distribution and 40\% had to rely completely on information from neighbors.
-
-\begin{figure*}[h]
-%\hspace*{0.1in}
-%\centerline{\includegraphics[scale=0.8]{figures/convergence_time}}
-\centering
-\includegraphics[width=.9\textwidth]{figures/convergence_time}
-\caption{Time to convergence as the size of the graph grows.
-Each datapoint is the average of 200 trials.
-For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=5$.
-DeGroot nodes were on average 20\% of the total vertices.
-Only 60\% of the Non-Bayesian nodes were receiving signals.
-We also show $R^2$ values for a linear regression for the different types of graph.
-We can see that the convergence time increases linearly with the size of the graph, and that the complete graph takes substantially longer to converge.
-}
-\label{fig:convergence_time}
-\end{figure*}
 

### 2012-12-12 docs/paper.tex
More typos.

@@
 It is clear that the DeGroot nodes essentially act as amplifiers, magnifying the initial belief updates of the Non-Bayesian nodes.
-This will in turn strengthen the Non-Bayesian's nodes beliefs in $\Theta^*$ (through Equation \ref{eq:non_bayesian_update}), which are then incorporated into the DeGroot nodes' parameter estimates.
+This will in turn strengthen the Non-Bayesian nodes beliefs in $\Theta^*$ (through Equation \ref{eq:non_bayesian_update}), which are then incorporated into the DeGroot nodes' parameter estimates.
 This feedback cycle increases the speed of convergence.
 
-In essence, this happens because belief estimation algorithm of the DeGroot nodes is inherently aggressive.
+In essence, this happens because the belief estimation algorithm of the DeGroot nodes is inherently aggressive.
 It is interesting to note that this can have negative effects on convergence when there is significant noise in the signal received by the Non-Bayesian nodes.

### 2012-12-12 docs/paper.tex
Corrected standard deviation

--- 2012-12-11 docs/paper.tex
@@
 Do certain network structures exacerbate their impact?
-How many naive agents can be present before learning becomes prohibitively difficult?
+How many naive agents can be present to significantly affect learning?
 In this work we investigate answers to these questions and propose our model of mixed Non-Bayesian and DeGroot learning as a tool for future research.
@@
 
+\begin{figure*}[t]
+%\hspace*{0.1in}
+%\centerline{\includegraphics[scale=0.8]{figures/nb_ratio}}
+\centering
+\includegraphics[width=0.9\textwidth]{figures/nb_ratio}
+\caption{Time to convergence as the ratio of Non-Bayesian to DeGroot nodes decreases.
+For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=1$.
+To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian nodes received any signals; the other 50\% needed to rely completely on learning from their neighbors.
+Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.
+Unexpectedly, the time to convergence is inversely proportional to the ratio of Non-Bayesian nodes.}
+\label{fig:nb_ratio}
+\end{figure*}
+
 \section{Convergence}
@@
 
+\begin{figure*}[t]
+%\hspace*{0.1in}
+%\centerline{\includegraphics[scale=0.8]{figures/convergence_time}}
+\centering
+\includegraphics[width=.9\textwidth]{figures/convergence_time}
+\caption{Time to convergence as the size of the graph grows.
+Each datapoint is the average of 200 trials.
+For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=1$.
+DeGroot nodes were on average 20\% of the total vertices.
+Only 60\% of the Non-Bayesian nodes were receiving signals.
+We also show $R^2$ values for a linear regression for the different types of graph.
+We can see that the convergence time increases linearly with the size of the graph, and that the complete graph takes substantially longer to converge.
+}
+\label{fig:convergence_time}
+\end{figure*}
+
 In order to seek insight about the behavior of our model we performed a series of simulations using the JUNG network/graph software library \cite{website:JUNGGraphLibrary}.
@@
 
-\begin{figure}[t]
-%\hspace*{0.1in}
-%\centerline{\includegraphics[scale=0.8]{figures/dg_faster}}
-\centering
-\includegraphics[width=0.48\textwidth]{figures/dg_faster}
-\caption{The average beliefs in $\Theta^*$, the true distribution, for the two types of nodes during simulations with 0\% and 20\% of DeGroot nodes in a complete graph.
-The possible distributions were Gaussians centered at 100 and 105 with $\sigma=1$.
-All random seeds were fixed such that in both runs the Non-Bayesian nodes received the exact same sequence of draws.
-DeGroot nodes' beliefs were estimated using the distance metric.
-The figure shows how DeGroot nodes help amplify the initial belief updates of Non-Bayesian nodes, which leads to overall faster convergence.}
-\label{fig:dg_faster}
-\end{figure}
-
 \subsection{Graph Size vs. Convergence Time}

### 2012-12-12 docs/paper.tex

--- 2012-12-12 docs/paper.tex
@@
 \caption{Time to convergence as the ratio of Non-Bayesian to DeGroot nodes decreases.
-For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=5$.
+For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=1$.
 To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian nodes received any signals; the other 50\% needed to rely completely on learning from their neighbors.
@@
 Each datapoint is the average of 200 trials.
-For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=5$.
+For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=1$.
 DeGroot nodes were on average 20\% of the total vertices.

### 2012-12-12 docs/paper.tex
Fixed lowercase fig reference

@@
 
-The results, shown in figure~\ref{fig:convergence_time}, show that time required for convergence appears to be linear with respect to the number of nodes in the graph.
+The results, shown in Figure~\ref{fig:convergence_time}, show that time required for convergence appears to be linear with respect to the number of nodes in the graph.
 

### 2012-12-12 docs/paper.tex
Lowercase'd thetas.

@@
 \includegraphics[width=0.9\textwidth]{figures/dg_faster}
-\caption{The average beliefs in $\Theta^*$, the true distribution, for the two types of nodes during simulations with 0\% and 20\% of DeGroot nodes in a complete graph.
+\caption{The average beliefs in $\theta^*$, the true distribution, for the two types of nodes during simulations with 0\% and 20\% of DeGroot nodes in a complete graph.
 The possible distributions were Gaussians centered at 100 and 105 with $\sigma=1$.
@@
 
-We can see this process in more detail in Figure~\ref{fig:dg_faster}, which shows the average beliefs in $\Theta^*$ for the intial steps of two trials on a complete graph.
+We can see this process in more detail in Figure~\ref{fig:dg_faster}, which shows the average beliefs in $\theta^*$ for the intial steps of two trials on a complete graph.
 It is clear that the DeGroot nodes essentially act as amplifiers, magnifying the initial belief updates of the Non-Bayesian nodes.
-This will in turn strengthen the Non-Bayesian nodes beliefs in $\Theta^*$ (through Equation \ref{eq:non_bayesian_update}), which are then incorporated into the DeGroot nodes' parameter estimates.
+This will in turn strengthen the Non-Bayesian nodes beliefs in $\theta^*$ (through Equation \ref{eq:non_bayesian_update}), which are then incorporated into the DeGroot nodes' parameter estimates.
 This feedback cycle increases the speed of convergence.
@@
 It is interesting to note that this can have negative effects on convergence when there is significant noise in the signal received by the Non-Bayesian nodes.
-If a Non-Bayesian node receives an ``unlucky'' draw that skews its belief distribution away from $\Theta^*$, this error will be amplified by the DeGroot nodes.
+If a Non-Bayesian node receives an ``unlucky'' draw that skews its belief distribution away from $\theta^*$, this error will be amplified by the DeGroot nodes.
 Since there was no noise in our simulations, the presence of DeGroot nodes is beneficial.

### 2012-12-12 docs/paper.tex
Explained why the complete graph takes longer to converge.

--- 2012-12-12 docs/paper.tex
@@
 
-The results, shown in Figure~\ref{fig:convergence_time}, show that time required for convergence appears to be linear with respect to the number of nodes in the graph.
+The results, presented in Figure~\ref{fig:convergence_time}, show that time required for convergence appears to be linear with respect to the number of nodes in the graph.
+Additionally, we can see that the complete graph takes longer to converge than the other graph types.
+This seems counter-intuitive at first: wouldn't a complete graph diffuse information more quickly, and threfore decrease the convergence time?
+The answer is that a complete graph has a large ``inertia''.
+To see that, imagine a graph comprised entirely of Non-Bayesian nodes that is trying to distinguish between two distributions $m_1$ and $m_2$.
+Let's say that node $i$ is the first one to receive a signal, and suppose that after the Bayesian update node $i$'s belief in $m_1$ is $p$.
+For the sake of concreteness, assume that $a_{ij}=1/(n+1)$ where $n$ is the number of node $i$'s neighbors.
+Then by Equation~\ref{eq:non_bayesian_update}:
+
+\begin{equation*}
+\mu_{i,t+1}(\theta_1) = \frac{p}{n+1} + \frac{n}{n+1}\left(\frac{1}{2}\right) = \frac{2p + n}{2n + 1} 
+\end{equation*}
+
+Therefore, as $n$ grows $\mu_{i,t+1}(\theta_1)$ tends towards 0.5.
+Naturally, there is a ripple effect: because node $i$'s belief update was attenuated, it will exert a smaller influence on its neighbors.
+This explains why the complete graph converges more slowly, since $n$ is larger than in any other graph type.
 

### 2012-12-12 docs/paper.tex
Math is hard!
A couple of typos.

@@
 
-We can see this process in more detail in Figure~\ref{fig:dg_faster}, which shows the average beliefs in $\theta^*$ for the intial steps of two trials on a complete graph.
+We can see this process in more detail in Figure~\ref{fig:dg_faster}, which shows the average beliefs in $\theta^*$ for the initial steps of two trials on a complete graph.
 It is clear that the DeGroot nodes essentially act as amplifiers, magnifying the initial belief updates of the Non-Bayesian nodes.
@@
 Additionally, we can see that the complete graph takes longer to converge than the other graph types.
-This seems counter-intuitive at first: wouldn't a complete graph diffuse information more quickly, and threfore decrease the convergence time?
+This seems counter-intuitive at first: wouldn't a complete graph diffuse information more quickly, and therefore decrease the convergence time?
 The answer is that a complete graph has a large ``inertia''.
@@
 \begin{equation*}
-\mu_{i,t+1}(\theta_1) = \frac{p}{n+1} + \frac{n}{n+1}\left(\frac{1}{2}\right) = \frac{2p + n}{2n + 1} 
+\mu_{i,t+1}(\theta_1) = \frac{p}{n+1} + \frac{n}{n+1}\left(\frac{1}{2}\right) = \frac{2p + n}{2n + 2} 
 \end{equation*}
